---
title: "EO-HEAT · Preview"
subtitle: "[ Method ] · [ HaoyuJiang ]"
output:
  xaringan::moon_reader:
    css: [default, custom.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: "16:9"
      countIncrementalSlides: false
      slideNumberFormat: "%current% / %total%"
---

```{r setup, include=FALSE}
# ══════════════════════════════════════════════════════
# 不需要修改这个 chunk，直接保留
# ══════════════════════════════════════════════════════
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE,
  fig.retina = 3, fig.align = "center"
)
```

```{r libraries, include=FALSE}
# ══════════════════════════════════════════════════════
# 在这里加载你需要的包
# 如果你不做地图，可以删掉 sf / tmap / rnaturalearth
# ══════════════════════════════════════════════════════
library(ggplot2)
library(scales)
library(showtext)

# 如需地图：
# library(sf)
# library(tmap)
# library(rnaturalearth)
# library(rnaturalearthdata)

# 如需 Venn 图：
# library(ggforce)

# 如需流程图：
# library(DiagrammeR)

font_add_google("Cormorant Garamond", "cormorant")
font_add_google("Outfit", "outfit")
showtext_auto()

# ── 共享主题（所有图表都用这个，不要修改）──────────────
theme_eoheat <- function(base_size = 12) {
  theme_minimal(base_family = "outfit", base_size = base_size) +
  theme(
    plot.background  = element_rect(fill = "#0F1117", color = NA),
    panel.background = element_rect(fill = "#0F1117", color = NA),
    panel.grid.major = element_line(color = "#252A40", linewidth = 0.4),
    panel.grid.minor = element_blank(),
    text             = element_text(color = "#9DA3B4"),
    axis.text        = element_text(color = "#5C6380", size = rel(0.82)),
    axis.title       = element_text(color = "#9DA3B4", size = rel(0.9)),
    plot.title       = element_text(color = "#EDE8DF", face = "bold",
                                    size = rel(1.15), margin = margin(b = 6)),
    plot.subtitle    = element_text(color = "#9DA3B4", size = rel(0.85),
                                    margin = margin(b = 12)),
    plot.caption     = element_text(color = "#5C6380", size = rel(0.7),
                                    hjust = 0, margin = margin(t = 8)),
    legend.background = element_rect(fill = "#0F1117", color = NA),
    legend.text      = element_text(color = "#9DA3B4"),
    legend.title     = element_text(color = "#EDE8DF"),
    plot.margin      = margin(12, 12, 12, 12)
  )
}
```

---



---
## Our Work Flow

.slide-label[Slide 1 · Method · HaoyuJiang]

.left-narrow[

### Method Overview 
>“Our approach integrates multi-source Earth Observation (EO) data with demographic and spatial information to quantify heat risk and vulnerability at the ward scale. The workflow consists of the following key stages”

**1: Data Acquisition **  
**2: Preprocessing**  
**3: Heat and Land Cover Mapping **
**4: Heat Vulnerability Assessment **  
**5: Spatial Inequality Analysis**  
**6: Policy-Relevant Outputs **  

]

.right-wide[

```{r fig-01-workflow, echo=FALSE, fig.height=6, fig.width=10}
library(DiagrammeR)

grViz("
digraph workflow {
  graph [layout = dot, rankdir = TB, bgcolor = '#0F1117', fontname = 'Helvetica', splines=polyline]

  node [shape = rectangle, style = filled, fontname = 'Helvetica', fontcolor = 'white', margin = 0.2]

  # Data Acquisition
  DA [label='Data Acquisition\\nLandsat 8/9, Sentinel-2, MODIS, Census, OSM', fillcolor='#2E86C1']

  # Preprocessing
  PP [label='Preprocessing\\nCloud Masking, Atmospheric Correction, Image Compositing, Spatial Alignment', fillcolor='#27AE60']

  # Analysis
  LULC [label='Vegetation & Land Cover', fillcolor='#C9A96E', fontcolor='#0F1117']
  UHI [label='UHI Intensity Mapping', fillcolor='#C9A96E', fontcolor='#0F1117']
  HVI [label='Heat Vulnerability Index', fillcolor='#C9A96E', fontcolor='#0F1117']
  SPA [label='Spatial Inequality Analysis', fillcolor='#C9A96E', fontcolor='#0F1117']

  # Outputs
  OUT [label='Outputs for Policy\\nWard-level Heat Maps, Priority Zones, Dashboard, Annual Monitoring', fillcolor='#8E44AD']

  # Connections (全部箭头白色)
  DA -> PP [color=white]
  PP -> LULC [color=white]
  PP -> UHI [color=white]
  LULC -> HVI [color=white]
  UHI -> HVI [color=white]
  DA -> HVI [style=dashed, color=white]
  DA -> SPA [style=dashed, color=white]
  HVI -> SPA [color=white]
  SPA -> OUT [color=white]
}
")
```
]
---
## Data Inputs and Their Role in Heat Risk Assessment

.slide-label[Slide 2 · Method · HaoyuJiang]

.left-narrow[

### Key Data Inputs

- **Satellite LST**  
  Multi-temporal LST from MODIS and Landsat 8/9 to identify urban heat islands and hotspots.

- **Land Cover & Vegetation**  
  Sentinel-2 NDVI / LULC data to analyze green space, built-up area, and impervious surfaces.

- **Population & Vulnerability Data**  
  Census and demographic indicators to assess exposure of vulnerable populations.

- **Street & Building Data**  
  OSM data to capture building density, street network, and their effects on heat distribution.
> "Accurate and multi-source data inputs are critical to model heat vulnerability at fine spatial scales."  

]

---
## Data Inputs and Their Role in Heat Risk Assessment

.slide-label[Slide 2 · Method · HaoyuJiang]

.left-narrow[

### Key Data Inputs

- **Satellite LST**  
  Multi-temporal LST from MODIS and Landsat 8/9 to identify urban heat islands and hotspots.

- **Land Cover & Vegetation**  
  Sentinel-2 NDVI / LULC data to analyze green space, built-up area, and impervious surfaces.

- **Population & Vulnerability Data**  
  Census and demographic indicators to assess exposure of vulnerable populations.

- **Street & Building Data**  
  OSM data to capture building density, street network, and their effects on heat distribution.
> "Accurate and multi-source data inputs are critical to model heat vulnerability at fine spatial scales."  

]
---
## Three Integrated Work Packages

.slide-label[Slide 3 · Method · HaoyuJiang]

.left-narrow[

### Three Integrated Work Packages 

**WP1: Heat Mapping**  
Generate multi-temporal LST maps to identify heat hotspots  


**WP2: Land Cover & Green Space**  
Analyze vegetation cover, built-up area, and impervious surfaces  


**WP3: Heat Vulnerability Index**  
Combine EO data with population, demographics, and building data to produce ward-level HVI  

]

.right-wide[

3 picture（heat，vage，indx）

]
```

---

<!--
╔══════════════════════════════════════════════════════╗
║  SLIDE 模板：流程图 / 概念图（DiagrammeR）             ║
║  适合：workflow、policy cascade、方法流程              ║
╚══════════════════════════════════════════════════════╝
-->

## Slide 标题写这里

.slide-label[Slide XX · 章节名 · 你的名字]

```{r fig-XX-diagram, fig.height=5.5, fig.width=11}
# ══════════════════════════════════════════════
# 📊 流程图 chunk（需要 library(DiagrammeR)）
# ══════════════════════════════════════════════
library(DiagrammeR)

grViz("
digraph workflow {
  graph [layout = dot, rankdir = LR, bgcolor = '#0F1117',
         fontname = 'Helvetica']
  
  node [fontname = 'Helvetica', shape = rectangle,
        style = filled, fontcolor = white, margin = 0.2]
  
  # 节点定义（fillcolor 用主题色）
  A [label = '步骤一',   fillcolor = '#2E86C1']
  B [label = '步骤二',   fillcolor = '#27AE60']
  C [label = '步骤三',   fillcolor = '#C9A96E', fontcolor = '#0F1117']
  D [label = '最终输出', fillcolor = '#8E44AD']
  
  # 连接关系
  A -> B -> C -> D
}
")
```


.footnote[参考文献]

---

<!--
╔══════════════════════════════════════════════════════╗
║  常用 CSS class 速查                                  ║
╠══════════════════════════════════════════════════════╣
║  布局                                                 ║
║  .pull-left[ ]        左半栏 (50%)                   ║
║  .pull-right[ ]       右半栏 (50%)                   ║
║  .left-wide[ ]        左宽栏 (60%)                   ║
║  .right-narrow[ ]     右窄栏 (36%)                   ║
║  .left-narrow[ ]      左窄栏 (36%)                   ║
║  .right-wide[ ]       右宽栏 (60%)                   ║
║                                                       ║
║  统计卡片                                             ║
║  .stat-box[ ]         金色左边框                      ║
║  .stat-box.alert[ ]   红色左边框                      ║
║  .stat-box.teal[ ]    青色左边框                      ║
║  .stats-row[ ]        横排卡片容器                    ║
║                                                       ║
║  文字颜色                                             ║
║  .text-gold            金色                           ║
║  .text-teal            青色                           ║
║  .text-muted           灰色                           ║
║  .text-small           小字                           ║
║                                                       ║
║  标签芯片                                             ║
║  .chip[ ]             灰色边框                        ║
║  .chip.gold[ ]        金色边框                        ║
║  .chip.teal[ ]        青色边框                        ║
║  .chip.alert[ ]       红色边框                        ║
║                                                       ║
║  政策色块（Slide 4 用）                               ║
║  .policy-global[ ]    蓝色                            ║
║  .policy-national[ ]  橙色                            ║
║  .policy-local[ ]     绿色                            ║
║  .policy-project[ ]   金色                            ║
╚══════════════════════════════════════════════════════╝
-->
