---
title: "EO-HEAT · Ahmedabad"
subtitle: "Approach · [你的名字]"
output:
  xaringan::moon_reader:
    css: [default, custom.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: "16:9"
      countIncrementalSlides: false
      slideNumberFormat: "%current% / %total%"
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE,
  fig.retina = 3, fig.align = "center"
)
```

```{r libraries, include=FALSE}
library(ggplot2)
library(scales)
library(showtext)
library(DiagrammeR)

font_add_google("Cormorant Garamond", "cormorant")
font_add_google("Outfit", "outfit")
showtext_auto()

theme_eoheat <- function(base_size = 12) {
  theme_minimal(base_family = "outfit", base_size = base_size) +
  theme(
    plot.background  = element_rect(fill = "#0F1117", color = NA),
    panel.background = element_rect(fill = "#0F1117", color = NA),
    panel.grid.major = element_line(color = "#252A40", linewidth = 0.4),
    panel.grid.minor = element_blank(),
    text             = element_text(color = "#9DA3B4"),
    axis.text        = element_text(color = "#5C6380", size = rel(0.82)),
    axis.title       = element_text(color = "#9DA3B4", size = rel(0.9)),
    plot.title       = element_text(color = "#EDE8DF", face = "bold",
                                    size = rel(1.15), margin = margin(b = 6)),
    plot.subtitle    = element_text(color = "#9DA3B4", size = rel(0.85),
                                    margin = margin(b = 12)),
    plot.caption     = element_text(color = "#5C6380", size = rel(0.7),
                                    hjust = 0, margin = margin(t = 8)),
    legend.background = element_rect(fill = "#0F1117", color = NA),
    legend.text      = element_text(color = "#9DA3B4"),
    legend.title     = element_text(color = "#EDE8DF"),
    plot.margin      = margin(12, 12, 12, 12)
  )
}
```

---

## Data Preprocessing

.left-wide[

```{r fig-pre-pipeline, fig.height=4.2, fig.width=7}
library(DiagrammeR)

grViz("
digraph preprocessing {
  graph [layout = dot, rankdir = TB, bgcolor = '#0F1117',
         fontname = 'Helvetica', nodesep = 0.4, ranksep = 0.45]

  node [fontname = 'Helvetica', shape = rectangle,
        style = filled, fontcolor = white,
        margin = '0.18,0.12', width = 2.2, fontsize = 12]

  subgraph cluster_sources {
    rank = same
    style = invis
    L8  [label = 'Landsat 8/9 TIRS LST',    fillcolor = '#2C3E6B', color = '#2C3E6B']
    S2  [label = 'Sentinel-2 MSI NDVI/LULC', fillcolor = '#2C3E6B', color = '#2C3E6B']
    MOD [label = 'MODIS LST Time Series',    fillcolor = '#2C3E6B', color = '#2C3E6B']
  }

  CM [label = 'Cloud Masking',          fillcolor = '#5D4037', color = '#5D4037']
  AC [label = 'Atmospheric Correction', fillcolor = '#5D4037', color = '#5D4037']
  IC [label = 'Image Compositing',      fillcolor = '#5D4037', color = '#5D4037']
  SA [label = 'Spatial Alignment',      fillcolor = '#C9A96E', color = '#C9A96E', fontcolor = '#0F1117']

  L8  -> CM [color = '#4FC4CF']
  S2  -> CM [color = '#4FC4CF']
  MOD -> CM [color = '#4FC4CF']

  CM -> AC [color = '#9DA3B4']
  AC -> IC [color = '#9DA3B4']
  IC -> SA [color = '#C9A96E', penwidth = 2]
}
")
```

.fig-caption[Fig. X · Preprocessing pipeline · Sources: GEE, USGS, ESA, NASA LP DAAC]

]

.right-narrow[

<style>
.right-narrow .stat-box {
  padding: 4px 8px 4px 12px !important;
  margin-bottom: 4px !important;
}
.right-narrow .stat-number {
  font-size: 0.95em !important;
  line-height: 1.1 !important;
  display: block !important;
  margin-bottom: 2px !important;
}
.right-narrow .stat-label {
  font-size: 0.68em !important;
  line-height: 1.25 !important;
  display: block !important;
}
.right-narrow .stat-source {
  font-size: 0.58em !important;
  display: block !important;
  margin-top: 2px !important;
}
</style>

.stat-box[
<span class="stat-number">Step 1</span>
<span class="stat-label">**Cloud Masking** — Remove pixels contaminated by cloud and shadow</span>
<span class="stat-source">Ensures only clear-sky data enters the pipeline</span>
]

.stat-box[
<span class="stat-number">Step 2</span>
<span class="stat-label">**Atmospheric Correction** — Strip out atmospheric interference to get true surface values</span>
<span class="stat-source">Critical for accurate LST in dusty conditions</span>
]

.stat-box[
<span class="stat-number">Step 3</span>
<span class="stat-label">**Image Compositing** — Merge multiple images into one clean seasonal snapshot</span>
<span class="stat-source">Reduces noise across the pre-monsoon period</span>
]

.stat-box[
<span class="stat-number">Step 4</span>
<span class="stat-label">**Spatial Alignment** — Stack all data layers onto a single shared grid</span>
<span class="stat-source">Enables pixel-level comparison across all sources</span>
]

]

.footnote[USGS Landsat Collection 2 · ESA Sentinel Hub · NASA LP DAAC · GEE Python API]

---

## Outputs for Policy

.stats-row[

.stat-box[
<span class="stat-number">01</span>
<span class="stat-label">**Ward-level Heat Maps**<br>
<span style="font-size:0.82em;color:#9DA3B4">
HVI (LST × 0.5 + Pop × 0.3 − NDVI × 0.2) overlaid with OSM data — identifies areas with the highest HVI scores
</span></span>
<span class="stat-source">Sources: Landsat LST · Sentinel-2 NDVI · Census · OSM</span>
]

.stat-box.teal[
<span class="stat-number">02</span>
<span class="stat-label">**Priority Intervention Zones**<br>
<span style="font-size:0.82em;color:#9DA3B4">
Derived from ward-level heat maps — flags areas with the highest combined heat and social vulnerability scores
</span></span>
]

.stat-box.alert[
<span class="stat-number">03</span>
<span class="stat-label">**Policy Dashboard Mockup**<br>
<span style="font-size:0.82em;color:#9DA3B4">
Static prototype linking ward heat scores to Ahmedabad Heat Action Plan targets
</span></span>
<span class="stat-source">Figma wireframe / R Shiny mockup</span>
]

.stat-box[
<span class="stat-number">04</span>
<span class="stat-label">**Annual Monitoring Plan**<br>
<span style="font-size:0.82em;color:#9DA3B4">
Repeatable GEE script for yearly LST updates across all wards
</span></span>
<span class="stat-source">Documented GEE code + update schedule</span>
]

]

<br>

> All four outputs feed directly into **Ahmedabad's Heat Action Plan (HAP)** — enabling evidence-based cooling investment at ward level.

.footnote[Ahmedabad HAP (2013) · Knowlton et al. (2014) PMC · SDG 11.6.2]

---

## Limitations

| Stage | Limitation | Consequence | Mitigation |
|-------|-----------|-------------|------------|
| **Data** | Landsat 16-day revisit cycle | Misses intra-heatwave LST peaks | Gap-fill with MODIS 8-day MOD11A2 |
| **Data** | WorldPop 2020 — 6-year lag from present | HVI may not reflect current population distribution | No newer high-resolution population dataset available via GEE |
| **Preprocessing** | Atmospheric correction uncertainty 1.6–2 K | Inflated LST in dust-storm events common in Ahmedabad | Apply MODTRAN coefficients validated for arid South Asia |
| **Preprocessing** | Monsoon cloud cover (JJA) leaves composite gaps | Incomplete seasonal stack for June–August | Restrict analysis to pre-monsoon (MAM) and post-monsoon (OND) |
| **Analysis** | 30 m resolution cannot resolve street-level micro-UHI | Priority zones generalised at ward scale only | — |

.stats-row[

.stat-box.alert[
<span class="stat-number">1.6–2 K</span>
<span class="stat-label">LST error, arid region</span>
<span class="stat-source">Emami & Mojaradi (2021)</span>
]

.stat-box[
<span class="stat-number">16 days</span>
<span class="stat-label">Landsat revisit gap</span>
<span class="stat-source">USGS Landsat Handbook</span>
]

.stat-box.teal[
<span class="stat-number">2020</span>
<span class="stat-label">WorldPop data lag</span>
<span class="stat-source">WorldPop (2020)</span>
]

]

.footnote[Emami & Mojaradi (2021) RSE · USGS Landsat Handbook · WorldPop (2020)]
