---
title: "EO-HEAT · Ahmedabad"
subtitle: "Approach · HaoyuJiang & [你的名字]"
output:
  xaringan::moon_reader:
    css: [default, custom.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: "16:9"
      countIncrementalSlides: false
      slideNumberFormat: "%current% / %total%"
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE,
  fig.retina = 3, fig.align = "center"
)
```

```{r libraries, include=FALSE}
library(ggplot2)
library(scales)
library(showtext)
library(DiagrammeR)

font_add_google("Cormorant Garamond", "cormorant")
font_add_google("Outfit", "outfit")
showtext_auto()

theme_eoheat <- function(base_size = 12) {
  theme_minimal(base_family = "outfit", base_size = base_size) +
  theme(
    plot.background  = element_rect(fill = "#0F1117", color = NA),
    panel.background = element_rect(fill = "#0F1117", color = NA),
    panel.grid.major = element_line(color = "#252A40", linewidth = 0.4),
    panel.grid.minor = element_blank(),
    text             = element_text(color = "#9DA3B4"),
    axis.text        = element_text(color = "#5C6380", size = rel(0.82)),
    axis.title       = element_text(color = "#9DA3B4", size = rel(0.9)),
    plot.title       = element_text(color = "#EDE8DF", face = "bold",
                                    size = rel(1.15), margin = margin(b = 6)),
    plot.subtitle    = element_text(color = "#9DA3B4", size = rel(0.85),
                                    margin = margin(b = 12)),
    plot.caption     = element_text(color = "#5C6380", size = rel(0.7),
                                    hjust = 0, margin = margin(t = 8)),
    legend.background = element_rect(fill = "#0F1117", color = NA),
    legend.text      = element_text(color = "#9DA3B4"),
    legend.title     = element_text(color = "#EDE8DF"),
    plot.margin      = margin(12, 12, 12, 12)
  )
}
```

---

## Our Workflow

.slide-label[Slide 1 · Overview · HaoyuJiang]

.left-narrow[

### Method Overview

> "Our approach integrates multi-source Earth Observation data with demographic and spatial information to quantify heat risk and vulnerability at the ward scale."

- **1 · Data Acquisition**
- **2 · Preprocessing**
- **3 · Heat & Vegetation Mapping**
- **4 · Ward-level HVI Construction**
- **5 · Spatial Inequality Analysis**
- **6 · Policy-Relevant Outputs**

]

.right-wide[

```{r fig-01-workflow, fig.height=5.5, fig.width=9}
library(DiagrammeR)

grViz("
digraph workflow {
  graph [layout = dot, rankdir = TB, bgcolor = '#0F1117',
         fontname = 'Helvetica', splines = polyline, nodesep = 0.4, ranksep = 0.5]

  node [shape = rectangle, style = filled, fontname = 'Helvetica',
        fontcolor = 'white', margin = 0.2, fontsize = 11]

  DA   [label = 'Data Acquisition\nLandsat 8/9 · Sentinel-2 · MODIS · WorldPop · OSM',
        fillcolor = '#2E86C1', color = '#2E86C1']
  PP   [label = 'Preprocessing\nCloud Masking · Atmospheric Correction · Compositing · Alignment',
        fillcolor = '#27AE60', color = '#27AE60']
  LULC [label = 'Vegetation Mapping', fillcolor = '#C9A96E', color = '#C9A96E', fontcolor = '#0F1117']
  HEAT [label = 'Surface Heat Mapping', fillcolor = '#C9A96E', color = '#C9A96E', fontcolor = '#0F1117']
  WARD [label = 'Ward-level Aggregation\nZonal Statistics', fillcolor = '#5D4037', color = '#5D4037']
  HVI  [label = 'Heat Vulnerability Index\n0.5×LST_norm + 0.3×Pop_norm − 0.2×NDVI_norm',
        fillcolor = '#C9A96E', color = '#C9A96E', fontcolor = '#0F1117']
  SPA  [label = 'Spatial Inequality Analysis\nIdentify high-risk ward clusters',
        fillcolor = '#C9A96E', color = '#C9A96E', fontcolor = '#0F1117']
  OUT  [label = 'Outputs for Policy\nHeat Maps · Priority Zones · Dashboard · Monitoring',
        fillcolor = '#8E44AD', color = '#8E44AD']

  DA   -> PP   [color = white]
  PP   -> LULC [color = white]
  PP   -> HEAT [color = white]
  LULC -> WARD [color = white]
  HEAT -> WARD [color = white]
  DA   -> WARD [style = dashed, color = white]
  WARD -> HVI  [color = white]
  HVI  -> SPA  [color = white]
  SPA  -> OUT  [color = white]
}
")
```

]

.footnote[Workflow adapted from IPCC AR5 exposure–sensitivity–adaptive capacity framework]

---

## Data Inputs and Their Role in Heat Risk Assessment

.slide-label[Slide 2 · Input · HaoyuJiang]

.left-narrow[

### Key Data Inputs

- **Satellite LST**
  MODIS for temporal continuity and gap-filling; Landsat 8/9 for higher-resolution ward-scale hotspot mapping

- **Land Cover & Vegetation**
  Sentinel-2 NDVI to analyse vegetation cover and green-space cooling effects

- **Population Data**
  WorldPop 2020 gridded population to assess exposure of vulnerable populations at ward scale

- **Spatial Context**
  OSM provides contextual layers for interpreting priority zones and communicating results

]

.right-wide[

```{r fig-02-inputs, fig.height=5, fig.width=8}
grViz("
digraph inputs {
  graph [layout = dot, rankdir = LR, bgcolor = '#0F1117',
         fontname = 'Helvetica', nodesep = 0.5, ranksep = 0.6]

  node [fontname = 'Helvetica', shape = rectangle, style = filled,
        fontcolor = white, margin = '0.2,0.12', fontsize = 11]

  L8  [label = 'Landsat 8/9\nTIRS LST',      fillcolor = '#2C3E6B', color = '#2C3E6B']
  S2  [label = 'Sentinel-2\nNDVI',           fillcolor = '#2C3E6B', color = '#2C3E6B']
  MOD [label = 'MODIS\nLST Time Series',     fillcolor = '#2C3E6B', color = '#2C3E6B']
  WP  [label = 'WorldPop 2020\nPopulation',  fillcolor = '#2C3E6B', color = '#2C3E6B']
  OSM [label = 'OSM\nSpatial Context',       fillcolor = '#2C3E6B', color = '#2C3E6B']

  LST [label = 'Surface Heat\nAnalysis',     fillcolor = '#5D4037', color = '#5D4037']
  VEG [label = 'Vegetation\nMapping',        fillcolor = '#5D4037', color = '#5D4037']
  POP [label = 'Population\nExposure',       fillcolor = '#5D4037', color = '#5D4037']
  CTX [label = 'Spatial\nInterpretation',    fillcolor = '#5D4037', color = '#5D4037']

  HVI [label = 'Ward-level Heat\nVulnerability Index', fillcolor = '#C9A96E', color = '#C9A96E', fontcolor = '#0F1117']

  L8  -> LST [color = '#4FC4CF']
  MOD -> LST [color = '#4FC4CF']
  S2  -> VEG [color = '#4FC4CF']
  WP  -> POP [color = '#4FC4CF']
  OSM -> CTX [color = '#4FC4CF']

  LST -> HVI [color = '#C9A96E']
  VEG -> HVI [color = '#C9A96E']
  POP -> HVI [color = '#C9A96E']
}
")
```

]

.footnote[USGS Landsat Collection 2 · ESA Sentinel Hub · NASA LP DAAC · WorldPop (2020) · OpenStreetMap]

---

## Data Preprocessing

.slide-label[Slide 3 · Preprocessing · Jianshu Wu]

.left-wide[

```{r fig-03-preprocess, fig.height=4.2, fig.width=7}
grViz("
digraph preprocessing {
  graph [layout = dot, rankdir = TB, bgcolor = '#0F1117',
         fontname = 'Helvetica', nodesep = 0.4, ranksep = 0.45]

  node [fontname = 'Helvetica', shape = rectangle, style = filled,
        fontcolor = white, margin = '0.18,0.12', width = 2.2, fontsize = 12]

  subgraph cluster_sources {
    rank = same
    style = invis
    L8  [label = 'Landsat 8/9 TIRS LST',    fillcolor = '#2C3E6B', color = '#2C3E6B']
    S2  [label = 'Sentinel-2 MSI NDVI',      fillcolor = '#2C3E6B', color = '#2C3E6B']
    MOD [label = 'MODIS LST Time Series',    fillcolor = '#2C3E6B', color = '#2C3E6B']
  }

  CM [label = 'Cloud Masking',          fillcolor = '#5D4037', color = '#5D4037']
  AC [label = 'Atmospheric Correction', fillcolor = '#5D4037', color = '#5D4037']
  IC [label = 'Image Compositing',      fillcolor = '#5D4037', color = '#5D4037']
  SA [label = 'Spatial Alignment',      fillcolor = '#C9A96E', color = '#C9A96E', fontcolor = '#0F1117']

  L8  -> CM [color = '#4FC4CF']
  S2  -> CM [color = '#4FC4CF']
  MOD -> CM [color = '#4FC4CF']
  CM  -> AC [color = '#9DA3B4']
  AC  -> IC [color = '#9DA3B4']
  IC  -> SA [color = '#C9A96E', penwidth = 2]
}
")
```

.fig-caption[Fig. 1 · Preprocessing pipeline · Sources: GEE, USGS, ESA, NASA LP DAAC]

]

.right-narrow[

<style>
.right-narrow .stat-box {
  padding: 4px 8px 4px 12px !important;
  margin-bottom: 4px !important;
}
.right-narrow .stat-number {
  font-size: 0.95em !important;
  line-height: 1.1 !important;
  display: block !important;
  margin-bottom: 2px !important;
}
.right-narrow .stat-label {
  font-size: 0.68em !important;
  line-height: 1.25 !important;
  display: block !important;
}
.right-narrow .stat-source {
  font-size: 0.58em !important;
  display: block !important;
  margin-top: 2px !important;
}
</style>

.stat-box[
<span class="stat-number">Step 1</span>
<span class="stat-label">**Cloud Masking** — Remove pixels contaminated by cloud and shadow</span>
<span class="stat-source">Ensures only clear-sky data enters the pipeline</span>
]

.stat-box[
<span class="stat-number">Step 2</span>
<span class="stat-label">**Atmospheric Correction** — Strip out atmospheric interference to get true surface values</span>
<span class="stat-source">Critical for accurate LST in dusty conditions</span>
]

.stat-box[
<span class="stat-number">Step 3</span>
<span class="stat-label">**Image Compositing** — Merge multiple images into one clean seasonal snapshot</span>
<span class="stat-source">Reduces noise across the pre-monsoon period</span>
]

.stat-box[
<span class="stat-number">Step 4</span>
<span class="stat-label">**Spatial Alignment** — Stack all data layers onto a single shared grid</span>
<span class="stat-source">Enables pixel-level comparison and ward-level aggregation</span>
]

]

.footnote[USGS Landsat Collection 2 · ESA Sentinel Hub · NASA LP DAAC · GEE Python API]

---

## Analysis: From Preprocessed Data to HVI

.slide-label[Slide 4 · Analysis · HaoyuJiang]

.left-narrow[

### Three Integrated Work Packages

**WP1 · Heat Mapping**
Generate multi-temporal LST maps to identify surface heat hotspots at ward scale

**WP2 · Vegetation Mapping**
Analyse vegetation cover and green-space cooling effects using Sentinel-2 NDVI

**WP3 · Heat Vulnerability Index**
Aggregate normalised indicators to ward boundaries using zonal statistics

> HVI = 0.5 × LST_norm + 0.3 × Pop_norm − 0.2 × NDVI_norm

.chip.gold[LST] .chip.teal[NDVI] .chip.alert[Population]

]

.right-wide[

```{r fig-04-analysis, fig.height=5, fig.width=8}
grViz("
digraph analysis {
  graph [layout = dot, rankdir = TB, bgcolor = '#0F1117',
         fontname = 'Helvetica', nodesep = 0.5, ranksep = 0.5]

  node [fontname = 'Helvetica', shape = rectangle, style = filled,
        fontcolor = white, margin = '0.2,0.12', fontsize = 11]

  PP   [label = 'Preprocessed Data Stack', fillcolor = '#27AE60', color = '#27AE60']

  subgraph rank_mid {
    rank = same
    VEG  [label = 'Vegetation\nMapping (WP2)', fillcolor = '#2C3E6B', color = '#2C3E6B']
    HEAT [label = 'Surface Heat\nMapping (WP1)', fillcolor = '#2C3E6B', color = '#2C3E6B']
  }

  WARD [label = 'Ward-level Aggregation\nZonal Statistics', fillcolor = '#5D4037', color = '#5D4037']

  HVI  [label = 'Heat Vulnerability Index (WP3)\n0.5×LST_norm + 0.3×Pop_norm − 0.2×NDVI_norm',
        fillcolor = '#C9A96E', color = '#C9A96E', fontcolor = '#0F1117']

  SPA  [label = 'Spatial Inequality Analysis\nCompare ward HVI · Identify high-risk clusters',
        fillcolor = '#8E44AD', color = '#8E44AD']

  PP   -> VEG  [color = '#4FC4CF']
  PP   -> HEAT [color = '#4FC4CF']
  VEG  -> WARD [color = '#C9A96E']
  HEAT -> WARD [color = '#C9A96E']
  WARD -> HVI  [color = '#C9A96E']
  HVI  -> SPA  [color = white, penwidth = 2]
}
")
```

]

.footnote[IPCC AR5 exposure–sensitivity–adaptive capacity framework · Kumar et al. (2024) · Chen et al. (2021)]

---

## Outputs for Policy

.slide-label[Slide 5 · Output · Jianshu Wu]

.stats-row[

.stat-box[
<span class="stat-number">01</span>
<span class="stat-label">**Ward-level Heat Maps**<br>
<span style="font-size:0.82em;color:#9DA3B4">
HVI (0.5×LST_norm + 0.3×Pop_norm − 0.2×NDVI_norm) overlaid with OSM context — identifies areas with highest HVI scores
</span></span>
<span class="stat-source">Sources: Landsat LST · Sentinel-2 NDVI · WorldPop · OSM</span>
]

.stat-box.teal[
<span class="stat-number">02</span>
<span class="stat-label">**Priority Intervention Zones**<br>
<span style="font-size:0.82em;color:#9DA3B4">
Derived from ward-level HVI maps — flags areas with the highest combined thermal and population exposure
</span></span>
]

.stat-box.alert[
<span class="stat-number">03</span>
<span class="stat-label">**Dashboard Mockup**<br>
<span style="font-size:0.82em;color:#9DA3B4">
Mockup to communicate ward-level HVI scores and intervention priorities
</span></span>
<span class="stat-source">Figma wireframe / R Shiny mockup</span>
]

.stat-box[
<span class="stat-number">04</span>
<span class="stat-label">**Annual Monitoring Plan**<br>
<span style="font-size:0.82em;color:#9DA3B4">
Workflow designed to be repeatable for annual LST updates across all wards
</span></span>
<span class="stat-source">Documented GEE code + update schedule</span>
]

]

<br>

> These outputs can inform **Ahmedabad's Heat Action Plan (HAP)** and support ward-level cooling prioritisation.

.footnote[Ahmedabad HAP (2013) · Knowlton et al. (2014) PMC · SDG 11.6.2]

---

## Limitations

.slide-label[Slide 6 · Limitations · Jianshu Wu]

| Stage | Limitation | Consequence | Mitigation |
|-------|-----------|-------------|------------|
| **Data** | WorldPop 2020 — 6-year lag | HVI may not reflect current population distribution | Best available proxy via GEE |
| **Preprocessing** | Atmospheric correction uncertainty 1.6–2 K | LST may be inflated under dusty conditions | Use region-appropriate correction parameters |
| **Analysis** | HVI is a simplified proxy — not a full vulnerability index | Socio-economic dimensions not captured | Interpret results as indicative only |
| **Analysis** | Weights derived from Kumar et al. (2024) correlations but rounded for simplicity | Ward rankings may shift under alternative weighting | Sensitivity testing in future work |

.stats-row[

.stat-box.alert[
<span class="stat-number">1.6–2 K</span>
<span class="stat-label">LST error, arid region</span>
<span class="stat-source">Emami & Mojaradi (2021)</span>
]

.stat-box[
<span class="stat-number">16 days</span>
<span class="stat-label">Landsat revisit gap</span>
<span class="stat-source">USGS Landsat Handbook</span>
]

.stat-box.teal[
<span class="stat-number">2020</span>
<span class="stat-label">WorldPop data lag</span>
<span class="stat-source">WorldPop (2020)</span>
]

]

.footnote[Emami & Mojaradi (2021) RSE · USGS Landsat Handbook · WorldPop (2020) · Kumar et al. (2024)]
