---
title: "EO-HEAT Ahmedabad"
subtitle: "Earth Observation for Heat Exposure Assessment and Targeted Mitigation"
author: "Terravance Advisory Group · CASA0023"
institute: "Centre for Advanced Spatial Analysis, UCL"
date: "2026"
output:
  xaringan::moon_reader:
    css: [default, custom.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: "16:9"
      countIncrementalSlides: false
      slideNumberFormat: "%current% / %total%"
      navigation:
        scroll: false
    seal: false
---
class: title-slide

<div style="position:absolute; top:10%; left:0; right:0; padding:2.5rem 4rem; border-top:1px solid rgba(201,169,110,0.5);">

<span style="display:inline-block; background:var(--bg-card); border:1px solid rgba(201,169,110,0.5); color:var(--gold); font-family:var(--font-body); font-size:0.7em; font-weight:500; letter-spacing:0.15em; text-transform:uppercase; padding:0.35em 0.9em; border-radius:2px; margin-bottom:1.2rem;">CASA0023 · Remotely Sensing Cities and Environments · 2026</span>

<h1 style="font-family:var(--font-display); font-size:3.4em; font-weight:700; color:var(--text-primary); line-height:1.05; margin:0 0 0.3em 0;">EO-HEAT<br>Ahmedabad</h1>

<h2 style="font-family:var(--font-body); font-size:1.05em; font-weight:300; color:var(--text-secondary); letter-spacing:0.03em; margin:0 0 1.5rem 0;">Earth Observation for Heat Exposure Assessment and Targeted Mitigation</h2>

<p style="font-family:var(--font-body); font-size:0.8em; font-weight:300; color:var(--text-muted); letter-spacing:0.08em; text-transform:uppercase; margin:0.2em 0;">Bidding to Ahmedabad Municipal Corporation (AMC)</p>
<p style="font-family:var(--font-body); font-size:0.8em; font-weight:300; color:var(--text-muted); letter-spacing:0.08em; text-transform:uppercase; margin:0.2em 0;">Terravance Advisory Group [TAG] · UCL CASA</p>
<p style="font-family:var(--font-body); font-size:0.8em; font-weight:300; color:var(--text-muted); letter-spacing:0.08em; text-transform:uppercase; margin:0.2em 0;">March 2026</p>

</div>
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE,
  fig.retina = 3, fig.align = "center"
)
```

```{r libraries, include=FALSE}
# install.packages(c("ggplot2","sf","tmap","rnaturalearth",
#                    "rnaturalearthdata","ggforce","showtext",
#                    "DiagrammeR","scales"))
library(ggplot2)
library(scales)
library(showtext)
font_add_google("Cormorant Garamond", "cormorant")   # ← 修正拼写
font_add_google("Outfit", "outfit")
showtext_auto()

# Shared ggplot theme for all figures
theme_eoheat <- function(base_size = 12) {
  theme_minimal(base_family = "outfit", base_size = base_size) +
  theme(
    plot.background  = element_rect(fill = "#0F1117", color = NA),
    panel.background = element_rect(fill = "#0F1117", color = NA),
    panel.grid.major = element_line(color = "#252A40", linewidth = 0.4),
    panel.grid.minor = element_blank(),
    text             = element_text(color = "#9DA3B4"),
    axis.text        = element_text(color = "#5C6380", size = rel(0.82)),
    axis.title       = element_text(color = "#9DA3B4", size = rel(0.9)),
    plot.title       = element_text(color = "#EDE8DF", face = "bold",
                                    size = rel(1.15), margin = margin(b = 6)),
    plot.subtitle    = element_text(color = "#9DA3B4", size = rel(0.85),
                                    margin = margin(b = 12)),
    plot.caption     = element_text(color = "#5C6380", size = rel(0.7),
                                    hjust = 0, margin = margin(t = 8)),
    legend.background = element_rect(fill = "#0F1117", color = NA),
    legend.text      = element_text(color = "#9DA3B4"),
    legend.title     = element_text(color = "#EDE8DF"),
    plot.margin      = margin(12, 12, 12, 12)
  )
}
```

---

## Presentation Structure

<br>

.pull-left[

.stat-box[
<span class="stat-number">01</span>
<span class="stat-label">Problem Definition</span>
<span class="stat-source">Slides 2–4 · ~2.5 min · 40% of marks</span>
]

.stat-box.teal[
<span class="stat-number">02</span>
<span class="stat-label">Approach & Methodology</span>
<span class="stat-source">Slides 5–10 · ~4 min · 40% of marks</span>
]

.stat-box[
<span class="stat-number">03</span>
<span class="stat-label">Project Plan & VFM</span>
<span class="stat-source">Slides 11–14 · ~2.5 min · 20% of marks</span>
]

]

.pull-right[

<br>

> Our proposal is structured around a single question:
>
> **How do we get the right intervention to the right ward, on the right day — before people die?**

<br>

.text-small.text-muted[
All figures in this presentation are produced from open-access  
Earth Observation data (Landsat 8/9, Sentinel-2, MODIS) unless  
otherwise noted. Code available at: `https://github.com/ArthurZhang69/CASA0023-GROUP-PRESENTATION.git`
]

]

---
class: section-slide

<span class="section-number">01 · Problem Definition</span>
# The Problem

---

## The Problem: Extreme Urban Heat Kills

.slide-label[Slide 02 · Problem Definition]

.left-wide[

```{r fig-a, fig.height=3.6, fig.width=7}
# ── Data Source ────────────────────────────────────────────────
# Built-up area: Chaturvedi et al. (2022) J. Geogr. Sci. 32:1791, Table 4
#   Landsat Maximum Likelihood Classification, 945 km² study area
# Population:
#   1990 / 2019 — Chaturvedi et al. (2022) / World Population Review
#   2001 / 2011 — Census of India (official)
# ───────────────────────────────────────────────────────────────
df <- data.frame(
  year       = c(1990, 2000,   2001,   2010,   2011,   2019),
  population = c(3.547, 4.519, 4.519,  5.578,  5.578,  7.868),
  builtup    = c(132.45, 181.55, NA,   276.46,  NA,    305.24)
)

df_builtup <- df[!is.na(df$builtup), ]

coeff <- 40

ggplot(df, aes(x = year)) +
  # Built-up area
  geom_area(data = df_builtup,
            aes(y = builtup / coeff),
            fill = "#C9A96E", alpha = 0.12) +
  geom_line(data = df_builtup,
            aes(y = builtup / coeff, color = "Built-up Area (km²)"),
            linewidth = 1.1, linetype = "dashed") +
  geom_point(data = df_builtup,
             aes(y = builtup / coeff, color = "Built-up Area (km²)"),
             size = 2.8, shape = 15) +
  # Population
  geom_line(aes(y = population, color = "Population (millions)"),
            linewidth = 1.4) +
  geom_point(aes(y = population, color = "Population (millions)"),
             size = 3.2, shape = 19) +
  # 2010 
  annotate("segment",
           x = 2010, xend = 2010,
           y = 0.3, yend = 6.2,
           color = "#E05C5C", linetype = "dotted", linewidth = 0.9) +
  annotate("label",
           x = 2010.2, y = 6.7,
           label = "May 2010\n1,344 deaths",
           fill = "#1E2235", color = "#E05C5C",
           size = 3.0, fontface = "bold", family = "outfit",
           label.padding = unit(0.35, "lines"),
           label.r = unit(0.2, "lines"), hjust = 0) +
  # 2000–2010 
  annotate("text",
           x = 2005, y = 4.3,
           label = "Fastest decade\n+52% built-up",
           color = "#C9A96E", size = 2.6,
           family = "outfit", fontface = "italic") +
  scale_y_continuous(
    name = "Population (millions)",
    limits = c(0, 9.5),
    sec.axis = sec_axis(~ . * coeff, name = "Built-up Area (km²)")
  ) +
  scale_x_continuous(breaks = c(1990, 2000, 2010, 2019)) +
  scale_color_manual(
    values = c("Population (millions)" = "#EDE8DF",
               "Built-up Area (km²)"   = "#C9A96E")
  ) +
  labs(
    title    = "Rapid urbanisation drives escalating heat risk",
    subtitle = "Ahmedabad population growth & built-up area expansion, 1990–2019",
    caption  = "Built-up area: Chaturvedi et al. (2022) J. Geogr. Sci. 32:1791, Table 4 (Landsat LULC classification)\nPopulation: Census of India (2001, 2011); World Population Review (2021)",
    x = NULL, color = NULL
  ) +
  theme_eoheat() +
  theme(
    legend.position    = c(0.2, 0.85),
    axis.title.y.right = element_text(color = "#C9A96E"),
    axis.title.y.left  = element_text(color = "#EDE8DF")
  )
```

.fig-caption[Fig. A · Built-up area: Chaturvedi et al. (2022) Table 4 · Population: Census of India]

]

<div class="right-narrow" style="margin-top:-2.5rem;">

.stat-box.alert[
<span class="stat-number">1,344</span>
<span class="stat-label">Excess deaths, May 2010</span>
<span class="stat-source">Azhar et al. (2014), PLOS ONE</span>
]

.stat-box[
<span class="stat-number">46.8°C</span>
<span class="stat-label">Peak temperature, May 25</span>
<span class="stat-source">IMD / Azhar et al. (2014)</span>
]

.stat-box[
<span class="stat-number">+130%</span>
<span class="stat-label">Built-up area growth, 1990–2019</span>
<span class="stat-source">Chaturvedi et al. (2022) Table 4</span>
]

.stat-box.teal[
<span class="stat-number">70%</span>
<span class="stat-label">of city area projected ≥45°C</span>
<span class="stat-source">Mohammad et al. (2022)</span>
]

</div>

.footnote[Azhar et al. (2014) *PLOS ONE* 9(3):e91831 · Chaturvedi et al. (2022) *J. Geogr. Sci.* 32:1791 · Mohammad et al. (2022) *J Water Clim Change*]

---

## Who Suffers Most? Heat Vulnerability is Unequal

.slide-label[Slide 03 · Problem Definition]

.pull-left[

```{r fig-c, fig.height=5.8, fig.width=5.8,dev.args=list(bg="#0F1117")}
library(ggforce)


circles <- data.frame(
  x    = c(-1.0,  1.0,  0.0),
  y    = c(-0.6, -0.6,  0.95),
  r    = c(2.0,   2.0,  2.0),
  fill = c("#C0392B", "#2980B9", "#27AE60")
)

ggplot() +
  geom_circle(data = circles,
              aes(x0 = x, y0 = y, r = r, fill = fill),
              alpha = 0.12, color = NA) +
  geom_circle(data = circles,
              aes(x0 = x, y0 = y, r = r, color = fill),
              linewidth = 1.0, fill = NA) +
  scale_fill_identity() +
  scale_color_identity() +

  annotate("text", x = -1.5, y = -1.5,
           label = "HAZARD\nHigh LST\nHeat Wave\nFrequency",
           size = 3.0, color = "#E05C5C",
           family = "outfit", fontface = "bold", lineheight = 1.35) +
  annotate("text", x = 1.5, y = -1.5,
           label = "EXPOSURE\nPopulation\nDensity\nOutdoor Workers",
           size = 3.0, color = "#5DADE2",
           family = "outfit", fontface = "bold", lineheight = 1.35) +
  annotate("text", x = 0.0, y = 2.05,
           label = "VULNERABILITY\nLow Income · Elderly\nMetal Roofs\nNo Greenery",
           size = 3.0, color = "#58D68D",
           family = "outfit", fontface = "bold", lineheight = 1.35) +
  annotate("text", x = 0, y = 0.12,
           label = "HEAT\nRISK",
           size = 5.2, fontface = "bold", family = "outfit",
           color = "white", lineheight = 1.2) +
  coord_equal(xlim = c(-4.2, 4.2), ylim = c(-3.5, 4.5)) +
  labs(
    title    = "Heat risk = Hazard × Exposure × Vulnerability",
    subtitle = "Adapted from IPCC AR6 WGII (2022), Chapter 8"
  ) +
  theme_void(base_family = "outfit") +
  theme(
    plot.background = element_rect(fill = "#0F1117", color = NA),
    plot.title      = element_text(color = "#EDE8DF", size = 11,
                                   face = "bold", hjust = 0.5,
                                   margin = margin(b = 4)),
    plot.subtitle   = element_text(color = "#5C6380", size = 8.5,
                                   hjust = 0.5, margin = margin(b = 8)),
    plot.margin     = margin(8, 8, 8, 8)
  )
```

.fig-caption[Fig. C · IPCC AR6 Risk Framework adapted for Ahmedabad]

]

.pull-right[

### Most exposed groups


| Group | Mechanism |
|-------|-----------|
| 🏚️ Slum communities | Metal roofs, no shade, no greenery |
| <span style="color:#EDE8DF">👷 Outdoor workers</span> | <span style="color:#9DA3B4">Direct thermal exposure, 8h+/day</span> |
| 👴 Elderly & infants | Impaired thermoregulation |
| <span style="color:#EDE8DF">💰 Low-income</span> | <span style="color:#9DA3B4">No AC, no access to cooling centres</span> |

<br>

> "The official temperature is recorded **8 km outside** the city. On the tarmac where workers walk, it can be **10°C hotter**."
>
> — Dr. Mavalankar, *Exemplars in Global Health* (2022)

.chip.alert[Spatial Data Gap] .chip[Ward-level] .chip.teal[1 Weather Station]

]

.footnote[IPCC AR6 WGII (2022) Ch.8 · Knowlton et al. (2014) *IJERPH* 11(4):3473 · Exemplars in Global Health (2022)]

---

## Policy Context: From Global Goals to Local Action

.slide-label[Slide 04 · Problem Definition]

.left-narrow[

.policy-global[
<span class="policy-label">🌍 Global</span>
**SDG** 3.9 · 11.5 · 11.7 · 13.1  
**Sendai Framework** Priority 1 & 3  
**New Urban Agenda** Para 37, 65, 79
]

<span style="font-size:0.8em;">↓</span>


.policy-national[
<span class="policy-label">🇮🇳 National</span>
**NAPCC** — Mission on Sustainable Habitat  
**India NDC 2022** — 33% urban green cover
]

<span style="font-size:0.8em;">↓</span>


.policy-local[
<span class="policy-label">🏙️ Local</span>
**Ahmedabad HAP 2019**  
~1,190 deaths averted / year
]


]

.right-wide[

### Ahmedabad Heat Action Plan (2019) — 4 Pillars

.stat-box[
<span class="stat-label">① Public Awareness & Community Outreach</span>
Multilingual pamphlets, WhatsApp alerts, LED boards, school campaigns
]

.stat-box[
<span class="stat-label">② Early Warning System</span>
Colour-coded heat alerts (Green → Red) triggered by IMD temperature thresholds
]

.stat-box[
<span class="stat-label">③ Medical Preparedness</span>
Heat stroke wards, ORS corners in all AMC hospitals, frontline worker training
]

.stat-box[
<span class="stat-label">④ Reduce Heat Exposure (Long-term)</span>
Cool Roofs Programme, 24hr park access, cooling centres for slum communities
]

<br>

> The HAP is pioneering — but all 4 pillars activate from **one weather station**. EO-HEAT provides the **ward-level spatial data** that makes every pillar more targeted.

]

.footnote[AMC / NRDC / IIPH-G (2019) *Ahmedabad HAP 2019* · Hess et al. (2018) *J Environ Public Health* · UNDRR (2015) Sendai Framework · UN (2017) New Urban Agenda]

---
class: section-slide

<span class="section-number">02 · Approach & Methodology</span>
# Our Approach

---

## Earth Observation & Ancillary Data

.slide-label[Slide 06 · Approach]

```{r fig-f, fig.height=3.8, fig.width=11}
datasets <- data.frame(
  name   = c("Landsat 8/9 TIRS", "Sentinel-2 MSI", "MODIS MOD11A2",
              "Census Ward Data", "OSM Buildings"),
  start  = c(1984, 2015, 2000, 2001, 2010),
  end    = c(2026, 2026, 2026, 2011, 2026),
  res    = c("30 m · 16-day", "10 m · 5-day", "1 km · 8-day",
             "Ward-level", "Building-level"),
  use    = c("Land Surface Temperature (LST)",
             "NDVI · Land Cover Classification",
             "Long-term LST trend (2000–2025)",
             "Demographics · Vulnerability Index",
             "Urban morphology · Imperviousness"),
  colour = c("#C9A96E", "#4FC4CF", "#E05C5C", "#58D68D", "#9DA3B4")
)

y_pos <- c(4, 3, 2, 1, 0)

ggplot(datasets) +
  geom_segment(aes(x = start, xend = end,
                   y = y_pos, yend = y_pos,
                   color = colour),
               linewidth = 5.5, lineend = "round") +
  geom_label(aes(x = start + 0.5, y = y_pos,
                 label = name, color = colour),
             fill = "#0F1117", size = 3.1,
             family = "outfit", fontface = "bold",
             label.padding = unit(0.3, "lines"),
             label.r = unit(0.15, "lines"), hjust = 0) +
  geom_text(aes(x = end - 0.5, y = y_pos + 0.55,
                label = res, color = colour),
            size = 2.5, family = "outfit", hjust = 1) +
  geom_text(aes(x = (start + end) / 2, y = y_pos - 0.45,
                label = use),
            color = "#5C6380", size = 2.6, family = "outfit") +
  scale_color_identity() +
  scale_x_continuous(breaks = seq(1985, 2025, 5),
                     expand = expansion(add = c(1, 2))) +
  labs(
    title    = "Multi-sensor, multi-temporal Earth Observation stack",
    subtitle = "All datasets free & analysis-ready via Google Earth Engine",
    x = NULL, y = NULL
  ) +
  theme_eoheat() +
  theme(axis.text.y = element_blank(),
        panel.grid.major.y = element_blank())
```

.fig-caption[Fig. F · EO Data Timeline · USGS / ESA / NASA / Census India / OpenStreetMap]

.footnote[All EO data accessed via Google Earth Engine · No licensing cost · Full temporal coverage from 1984]

---
class: section-slide

<span class="section-number">03 · Project Plan</span>
# Project Plan &amp; Value for Money

---

## Project Timeline(纯演示)

.slide-label[Slide 13 · Project Plan]

```{r gantt, fig.height=4.5, fig.width=11}
tasks <- data.frame(
  wp   = c("WP0 Inception","WP0 Inception",
           "WP1 LST Mapping","WP1 LST Mapping","WP1 LST Mapping",
           "WP2 Land Cover","WP2 Land Cover","WP2 Land Cover",
           "WP3 HVI","WP3 HVI",
           "WP4 Dashboard","WP4 Dashboard",
           "WP5 Training","WP6 M&E"),
  task = c("Kick-off & stakeholder setup","Data access agreements",
           "GEE pipeline development","LST composite & trend",
           "UHI intensity mapping",
           "Training data collection","RF classification","NDVI-LST regression",
           "Census data integration","HVI construction",
           "GEE App development","Report & dissemination",
           "AMC staff training","Monitoring & evaluation"),
  start = c(1,1, 2,3,4, 3,4,5, 6,7, 7,8, 9,10),
  end   = c(2,2, 3,5,5, 5,6,6, 7,8, 9,9, 10,12),
  col   = c("#5C6380","#5C6380",
            "#C9A96E","#C9A96E","#C9A96E",
            "#4FC4CF","#4FC4CF","#4FC4CF",
            "#58D68D","#58D68D",
            "#E05C5C","#E05C5C",
            "#9B59B6","#F0A04B")
)
milestones <- data.frame(
  x = c(5, 6, 8, 10, 12),
  y = c("WP1 LST Mapping","WP2 Land Cover",
        "WP3 HVI","WP5 Training","WP6 M&E")
)
tasks$task <- factor(tasks$task, levels = rev(unique(tasks$task)))

ggplot(tasks, aes(y = task)) +
  geom_segment(aes(x = start - 0.08, xend = end + 0.08,
                   yend = task, color = col),
               linewidth = 5, lineend = "round") +
  geom_point(data = milestones,
             aes(x = x, y = y),
             shape = 18, size = 3.5, color = "#EDE8DF",
             inherit.aes = FALSE) +
  scale_color_identity() +
  scale_x_continuous(breaks = 1:12,
                     labels = paste0("M", 1:12),
                     expand = expansion(add = 0.5)) +
  labs(
    title    = "12-month project schedule — 6 work packages",
    subtitle = "◆ = key milestone / deliverable",
    x = "Month", y = NULL
  ) +
  theme_eoheat(base_size = 10) +
  theme(panel.grid.major.y = element_blank(),
        axis.text.y = element_text(size = 8, color = "#9DA3B4"))
```

.footnote[★ M1: AMC Kick-off · ★ M5: LST maps delivered · ★ M8: HVI delivered · ★ M10: Training complete · ★ M12: Final presentation]

---

## Summary: Why EO-HEAT Ahmedabad?

.slide-label[Slide 15 · Summary]

<br>

.stats-row[

.stat-box.alert[
<span class="stat-number">1,344</span>
<span class="stat-label">Deaths in one month (2010)</span>
<span class="stat-source">The problem we are solving</span>
]

.stat-box.teal[
<span class="stat-number">1,190</span>
<span class="stat-label">Deaths averted/yr by HAP</span>
<span class="stat-source">What good policy can do</span>
]

.stat-box[
<span class="stat-number">Ward</span>
<span class="stat-label">Level spatial precision</span>
<span class="stat-source">What the HAP currently lacks</span>
]

.stat-box[
<span class="stat-number">£500k</span>
<span class="stat-label">Total project cost</span>
<span class="stat-source">Self-sustaining after Year 1</span>
]

]

<br>

.pull-left[

.checklist[
- **Evidence-based**: First ward-level Heat Vulnerability Index for Ahmedabad from multi-sensor EO
- **Policy-ready**: Direct input to HAP annual updates + SDG 11/13 reporting
- **Sustainable**: GEE pipeline runs at near-zero marginal cost post-handover
]

]

.pull-right[

> "For £500,000, we deliver not just a one-time assessment, but a **self-sustaining monitoring system** that will protect Ahmedabad's most vulnerable residents from deadly heat — for years to come."

<br>

.mono.text-small.text-muted[
github.com/[team]/eo-heat · UCL CASA · 2026
]

]

---
class: final-slide

<div style="display:flex; flex-direction:column; align-items:center; justify-content:center; height:100%; padding:3rem 4rem;">

<h1 style="font-family:var(--font-display); color:var(--text-primary); margin:0 0 0.2em 0;">Thank You</h1>
<p style="font-family:var(--font-body); color:var(--text-muted); letter-spacing:0.15em; text-transform:uppercase; font-size:0.8em; margin:0 0 2.5rem 0;">Questions Welcome</p>

<div style="display:flex; gap:1.5rem; width:100%; max-width:900px; margin-bottom:2rem;">

<div style="flex:1; background:var(--bg-card); border:1px solid var(--border); border-radius:4px; padding:1.2rem;">
<p style="font-family:var(--font-body); color:var(--gold); font-size:0.65em; letter-spacing:0.18em; text-transform:uppercase; margin:0 0 0.5rem 0;">Project Lead</p>
<p style="color:var(--text-primary); margin:0 0 0.3rem 0;">Member A</p>
<p style="font-family:var(--font-mono); color:var(--text-muted); font-size:0.75em; margin:0;">a.member@ucl.ac.uk</p>
</div>

<div style="flex:1; background:var(--bg-card); border:1px solid var(--border); border-radius:4px; padding:1.2rem;">
<p style="font-family:var(--font-body); color:var(--gold); font-size:0.65em; letter-spacing:0.18em; text-transform:uppercase; margin:0 0 0.5rem 0;">EO Analysis</p>
<p style="color:var(--text-primary); margin:0 0 0.3rem 0;">Member B</p>
<p style="font-family:var(--font-mono); color:var(--text-muted); font-size:0.75em; margin:0;">b.member@ucl.ac.uk</p>
</div>

<div style="flex:1; background:var(--bg-card); border:1px solid var(--border); border-radius:4px; padding:1.2rem;">
<p style="font-family:var(--font-body); color:var(--teal); font-size:0.65em; letter-spacing:0.18em; text-transform:uppercase; margin:0 0 0.5rem 0;">Repository</p>
<p style="color:var(--text-primary); margin:0 0 0.3rem 0;">All code &amp; data</p>
<p style="font-family:var(--font-mono); color:var(--text-muted); font-size:0.75em; margin:0;">github.com/[team]/eo-heat</p>
</div>

</div>

<p style="font-family:var(--font-body); color:var(--text-muted); font-size:0.7em; text-align:center; margin:0;">CASA0023 · Remotely Sensing Cities and Environments · UCL 2026<br>Slides produced with Xaringan · R · ggplot2 · All EO data via Google Earth Engine</p>

</div>
