---
title: "EO-HEAT Ahmedabad — Slides 13–15"
subtitle: "Project Plan, Risk Register & Summary"
author: "ZheXiang Zhou · Person E"
output:
  xaringan::moon_reader:
    css: [default, "../custom.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: "16:9"
      countIncrementalSlides: false
      slideNumberFormat: "%current% / %total%"
      navigation:
        scroll: false
    seal: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE,
  fig.retina = 3, fig.align = "center"
)
```

```{r libraries, include=FALSE}
library(ggplot2)
library(scales)
library(showtext)
font_add_google("Cormorant Garamond", "cormorant")
font_add_google("Outfit", "outfit")
showtext_auto()

theme_eoheat <- function(base_size = 12) {
  theme_minimal(base_family = "outfit", base_size = base_size) +
  theme(
    plot.background  = element_rect(fill = "#0F1117", color = NA),
    panel.background = element_rect(fill = "#0F1117", color = NA),
    panel.grid.major = element_line(color = "#252A40", linewidth = 0.4),
    panel.grid.minor = element_blank(),
    text             = element_text(color = "#9DA3B4"),
    axis.text        = element_text(color = "#5C6380", size = rel(0.82)),
    axis.title       = element_text(color = "#9DA3B4", size = rel(0.9)),
    plot.title       = element_text(color = "#EDE8DF", face = "bold",
                                    size = rel(1.15), margin = margin(b = 6)),
    plot.subtitle    = element_text(color = "#9DA3B4", size = rel(0.85),
                                    margin = margin(b = 12)),
    plot.caption     = element_text(color = "#5C6380", size = rel(0.7),
                                    hjust = 0, margin = margin(t = 8)),
    legend.background = element_rect(fill = "#0F1117", color = NA),
    legend.text      = element_text(color = "#9DA3B4"),
    legend.title     = element_text(color = "#EDE8DF"),
    plot.margin      = margin(12, 12, 12, 12)
  )
}
```

---

## Project Timeline & Budget

.slide-label[Slide 13 · Project Plan]

.left-wide[

```{r gantt-chart, fig.height=4.2, fig.width=8}
library(dplyr)

tasks <- data.frame(
  wp    = factor(rep(c("WP0 Scoping", "WP1 LST", "WP2 Land Cover",
                        "WP3 HVI", "WP4 Dashboard", "WP5 Handover"),
                      c(2, 3, 3, 2, 2, 2)),
                 levels = rev(c("WP0 Scoping", "WP1 LST", "WP2 Land Cover",
                                "WP3 HVI", "WP4 Dashboard", "WP5 Handover"))),
  task  = c("Stakeholder scoping", "Data audit & access",
            "GEE pipeline dev", "LST composite & trend", "UHI intensity map",
            "Training data", "RF classification", "NDVI-LST regression",
            "Census integration", "HVI construction & validation",
            "GEE App & report", "Dissemination",
            "AMC staff training", "BAU setup & handover"),
  start = c(1, 1,   2, 3, 4,   3, 4, 5,   5, 6,   7, 8,   9, 10),
  end   = c(2, 2,   3, 5, 5,   5, 6, 6,   7, 8,   9, 10,  11, 12),
  col   = rep(c("#5C6380", "#C9A96E", "#4FC4CF",
                "#58D68D", "#E05C5C", "#9B59B6"), c(2, 3, 3, 2, 2, 2))
)

tasks$task <- factor(tasks$task, levels = rev(tasks$task))

# Milestones
ms <- data.frame(
  x     = c(2,     6,     8,     10,    12),
  label = c("Data Audit\nComplete",
            "LST & LULC\nMaps Done",
            "HVI Map\nDelivered",
            "Dashboard\nBeta",
            "Final\nHandover"),
  y     = c(13, 9, 5, 3, 1)
)

ggplot(tasks, aes(y = task)) +
  # Phase background bands
  annotate("rect", xmin = 0.5, xmax = 2.5,
           ymin = 0.3, ymax = 14.7,
           fill = "#5C6380", alpha = 0.04) +
  annotate("rect", xmin = 2.5, xmax = 6.5,
           ymin = 0.3, ymax = 14.7,
           fill = "#C9A96E", alpha = 0.04) +
  annotate("rect", xmin = 6.5, xmax = 10.5,
           ymin = 0.3, ymax = 14.7,
           fill = "#E05C5C", alpha = 0.04) +
  annotate("rect", xmin = 10.5, xmax = 12.5,
           ymin = 0.3, ymax = 14.7,
           fill = "#9B59B6", alpha = 0.04) +
  # Task bars
  geom_segment(aes(x = start - 0.05, xend = end + 0.05,
                   yend = task, color = col),
               linewidth = 4.5, lineend = "round") +
  # Milestone diamonds
  geom_point(data = ms, aes(x = x, y = y),
             shape = 18, size = 4, color = "#EDE8DF",
             inherit.aes = FALSE) +
  # Milestone labels
  geom_text(data = ms, aes(x = x, y = y + 0.7, label = label),
            color = "#EDE8DF", size = 1.9, family = "outfit",
            fontface = "bold", lineheight = 0.9,
            inherit.aes = FALSE) +
  # WP labels on right margin
  scale_color_identity() +
  scale_x_continuous(breaks = 1:12,
                     labels = paste0("M", 1:12),
                     limits = c(0.5, 12.5),
                     expand = expansion(add = 0)) +
  labs(
    title    = "12-month project schedule",
    subtitle = "6 work packages · 14 tasks · 5 key milestones (◆)",
    x = NULL, y = NULL
  ) +
  theme_eoheat(base_size = 9) +
  theme(panel.grid.major.y = element_blank(),
        axis.text.y = element_text(size = 7, color = "#9DA3B4",
                                   hjust = 1))
```

.fig-caption[Fig. P · Gantt chart: WP0–WP5 with milestone diamonds]

]

<div class="right-narrow" style="margin-top: -1rem;">

### Budget · £500,000

```{r donut-chart, fig.height=3.2, fig.width=3.8, dev.args=list(bg="#0F1117")}
budget <- data.frame(
  category = c("Personnel", "Local Partner", "Software & Cloud",
               "Stakeholder\nEngagement", "Training", "Reporting",
               "Contingency"),
  amount   = c(280, 50, 20, 45, 30, 15, 60),
  fill     = c("#C9A96E", "#4FC4CF", "#5DADE2",
               "#58D68D", "#9B59B6", "#F0A04B", "#5C6380")
)

budget$pct <- budget$amount / sum(budget$amount) * 100
budget$label <- paste0(budget$category, "\n£", budget$amount, "k")

# Compute positions for labels
budget <- budget %>%
  arrange(desc(row_number())) %>%
  mutate(
    ymax = cumsum(amount),
    ymin = lag(ymax, default = 0),
    ymid = (ymin + ymax) / 2
  )

# Donut chart
ggplot(budget, aes(ymax = ymax, ymin = ymin, xmax = 4, xmin = 2.5, fill = fill)) +
  geom_rect(color = "#0F1117", linewidth = 0.6) +
  geom_text(aes(x = 3.25, y = ymid,
                label = paste0(round(pct), "%")),
            color = "#0F1117", size = 2.5,
            family = "outfit", fontface = "bold") +
  geom_text(aes(x = 4.8, y = ymid,
                label = paste0("£", amount, "k")),
            color = "#9DA3B4", size = 2.2,
            family = "outfit", hjust = 0) +
  # Centre label
  annotate("text", x = 0, y = 250,
           label = "£500k", color = "#EDE8DF",
           size = 4, family = "cormorant", fontface = "bold") +
  annotate("text", x = 0, y = 210,
           label = "Total", color = "#5C6380",
           size = 2.5, family = "outfit") +
  scale_fill_identity() +
  coord_polar(theta = "y") +
  xlim(c(0, 5.5)) +
  theme_void(base_family = "outfit") +
  theme(
    plot.background = element_rect(fill = "#0F1117", color = NA),
    plot.margin = margin(2, 2, 2, 2)
  )
```

<div style="font-size:0.62em; color:#9DA3B4; line-height:1.55; margin-top:0.3rem;">

| Item | £k | % |
|------|----|---|
| Personnel (2 RS + 1 GIS + 1 PM) | 280 | 56 |
| Local partner (AMC) | 50 | 10 |
| Stakeholder engagement | 45 | 9 |
| Capacity building | 30 | 6 |
| Software & cloud | 20 | 4 |
| Reporting | 15 | 3 |
| **Contingency** | **60** | **12** |

</div>

</div>

.footnote[Personnel cost 56% typical for technical consultancy · 12% contingency follows DFID best practice · All EO data & GEE compute at zero licence cost]

---

## Risk Register

.slide-label[Slide 14 · Project Plan]

<div style="font-size:0.78em; margin-top:-0.3rem;">

<table style="width:100%; border-collapse:collapse; font-size:0.95em;">
<thead>
<tr style="background:#252A40;">
  <th style="padding:0.5rem 0.6rem; color:#C9A96E; font-size:0.75em; letter-spacing:0.1em; text-transform:uppercase; width:3%;">#</th>
  <th style="padding:0.5rem 0.6rem; color:#C9A96E; font-size:0.75em; letter-spacing:0.1em; text-transform:uppercase; width:24%;">Risk</th>
  <th style="padding:0.5rem 0.6rem; color:#C9A96E; font-size:0.75em; letter-spacing:0.1em; text-transform:uppercase; width:10%; text-align:center;">Likelihood</th>
  <th style="padding:0.5rem 0.6rem; color:#C9A96E; font-size:0.75em; letter-spacing:0.1em; text-transform:uppercase; width:10%; text-align:center;">Impact</th>
  <th style="padding:0.5rem 0.6rem; color:#C9A96E; font-size:0.75em; letter-spacing:0.1em; text-transform:uppercase; width:53%;">Mitigation Strategy</th>
</tr>
</thead>
<tbody>
<tr style="background:rgba(224,92,92,0.08); border-bottom:1px solid rgba(201,169,110,0.15);">
  <td style="padding:0.45rem 0.6rem; color:#EDE8DF; font-weight:500;">R1</td>
  <td style="padding:0.45rem 0.6rem; color:#EDE8DF;">Cloud cover limits usable Landsat / Sentinel scenes</td>
  <td style="padding:0.45rem 0.6rem; text-align:center;"><span style="background:#F0A04B; color:#0F1117; padding:0.15em 0.5em; border-radius:2px; font-size:0.82em; font-weight:600;">Med</span></td>
  <td style="padding:0.45rem 0.6rem; text-align:center;"><span style="background:#E05C5C; color:#0F1117; padding:0.15em 0.5em; border-radius:2px; font-size:0.82em; font-weight:600;">High</span></td>
  <td style="padding:0.45rem 0.6rem; color:#9DA3B4;">Use pre-monsoon window (Mar–May, <15% cloud); supplement with MODIS 8-day composites for gap-filling</td>
</tr>
<tr style="background:rgba(79,196,207,0.05); border-bottom:1px solid rgba(201,169,110,0.15);">
  <td style="padding:0.45rem 0.6rem; color:#EDE8DF; font-weight:500;">R2</td>
  <td style="padding:0.45rem 0.6rem; color:#EDE8DF;">Census ward boundaries change between cycles</td>
  <td style="padding:0.45rem 0.6rem; text-align:center;"><span style="background:#58D68D; color:#0F1117; padding:0.15em 0.5em; border-radius:2px; font-size:0.82em; font-weight:600;">Low</span></td>
  <td style="padding:0.45rem 0.6rem; text-align:center;"><span style="background:#F0A04B; color:#0F1117; padding:0.15em 0.5em; border-radius:2px; font-size:0.82em; font-weight:600;">Med</span></td>
  <td style="padding:0.45rem 0.6rem; color:#9DA3B4;">Use AMC's latest administrative shapefile; build spatial harmonisation routine in GEE for boundary alignment</td>
</tr>
<tr style="background:rgba(224,92,92,0.08); border-bottom:1px solid rgba(201,169,110,0.15);">
  <td style="padding:0.45rem 0.6rem; color:#EDE8DF; font-weight:500;">R3</td>
  <td style="padding:0.45rem 0.6rem; color:#EDE8DF;">AMC staff turnover disrupts BAU adoption</td>
  <td style="padding:0.45rem 0.6rem; text-align:center;"><span style="background:#F0A04B; color:#0F1117; padding:0.15em 0.5em; border-radius:2px; font-size:0.82em; font-weight:600;">Med</span></td>
  <td style="padding:0.45rem 0.6rem; text-align:center;"><span style="background:#E05C5C; color:#0F1117; padding:0.15em 0.5em; border-radius:2px; font-size:0.82em; font-weight:600;">High</span></td>
  <td style="padding:0.45rem 0.6rem; color:#9DA3B4;">Train 5+ staff across 2 departments; deliver Standard Operating Procedure (SOP) documentation & video tutorials</td>
</tr>
<tr style="background:rgba(79,196,207,0.05); border-bottom:1px solid rgba(201,169,110,0.15);">
  <td style="padding:0.45rem 0.6rem; color:#EDE8DF; font-weight:500;">R4</td>
  <td style="padding:0.45rem 0.6rem; color:#EDE8DF;">Budget overrun on personnel costs</td>
  <td style="padding:0.45rem 0.6rem; text-align:center;"><span style="background:#58D68D; color:#0F1117; padding:0.15em 0.5em; border-radius:2px; font-size:0.82em; font-weight:600;">Low</span></td>
  <td style="padding:0.45rem 0.6rem; text-align:center;"><span style="background:#E05C5C; color:#0F1117; padding:0.15em 0.5em; border-radius:2px; font-size:0.82em; font-weight:600;">High</span></td>
  <td style="padding:0.45rem 0.6rem; color:#9DA3B4;">Fixed-term contracts with capped day-rates; 12% contingency reserve (£60k) ring-fenced for overruns</td>
</tr>
<tr style="background:rgba(224,92,92,0.08); border-bottom:1px solid rgba(201,169,110,0.15);">
  <td style="padding:0.45rem 0.6rem; color:#EDE8DF; font-weight:500;">R5</td>
  <td style="padding:0.45rem 0.6rem; color:#EDE8DF;">Stakeholder disengagement delays feedback</td>
  <td style="padding:0.45rem 0.6rem; text-align:center;"><span style="background:#F0A04B; color:#0F1117; padding:0.15em 0.5em; border-radius:2px; font-size:0.82em; font-weight:600;">Med</span></td>
  <td style="padding:0.45rem 0.6rem; text-align:center;"><span style="background:#F0A04B; color:#0F1117; padding:0.15em 0.5em; border-radius:2px; font-size:0.82em; font-weight:600;">Med</span></td>
  <td style="padding:0.45rem 0.6rem; color:#9DA3B4;">Embed AMC liaison officer in project team from M1; quarterly review meetings with ward councillors</td>
</tr>
<tr style="background:rgba(79,196,207,0.05); border-bottom:1px solid rgba(201,169,110,0.15);">
  <td style="padding:0.45rem 0.6rem; color:#EDE8DF; font-weight:500;">R6</td>
  <td style="padding:0.45rem 0.6rem; color:#EDE8DF;">LST retrieval accuracy insufficient at ward scale</td>
  <td style="padding:0.45rem 0.6rem; text-align:center;"><span style="background:#58D68D; color:#0F1117; padding:0.15em 0.5em; border-radius:2px; font-size:0.82em; font-weight:600;">Low</span></td>
  <td style="padding:0.45rem 0.6rem; text-align:center;"><span style="background:#F0A04B; color:#0F1117; padding:0.15em 0.5em; border-radius:2px; font-size:0.82em; font-weight:600;">Med</span></td>
  <td style="padding:0.45rem 0.6rem; color:#9DA3B4;">Cross-validate Landsat LST with MODIS MOD11A2 & IMD ground station records; report RMSE per ward</td>
</tr>
</tbody>
</table>

</div>

<br>

.stats-row[

.stat-box[
<span class="stat-number" style="font-size:1.4em;">2</span>
<span class="stat-label">High-impact risks</span>
<span class="stat-source">R1 Cloud cover · R3 Staff turnover</span>
]

.stat-box.teal[
<span class="stat-number" style="font-size:1.4em;">6</span>
<span class="stat-label">Dimensions covered</span>
<span class="stat-source">Data · Admin · Personnel · Budget · Stakeholder · Technical</span>
]

.stat-box[
<span class="stat-number" style="font-size:1.4em;">12%</span>
<span class="stat-label">Contingency reserve</span>
<span class="stat-source">£60k ring-fenced · DFID best practice</span>
]

]

.footnote[Risk matrix: <span style="background:#E05C5C; color:#0F1117; padding:0.1em 0.4em; border-radius:2px; font-size:0.9em;">High</span> <span style="background:#F0A04B; color:#0F1117; padding:0.1em 0.4em; border-radius:2px; font-size:0.9em;">Medium</span> <span style="background:#58D68D; color:#0F1117; padding:0.1em 0.4em; border-radius:2px; font-size:0.9em;">Low</span> · All mitigations are operationalised in project SOP]

---

## Summary: Why EO-HEAT Ahmedabad?

.slide-label[Slide 15 · Summary & Call to Action]

<br>

<div style="display:flex; gap:1.2rem; margin:0.8rem 0 1.5rem 0;">

<div style="flex:1; background:#1E2235; border:1px solid rgba(201,169,110,0.2); border-top:3px solid #C9A96E; border-radius:0 0 4px 4px; padding:1.2rem 1rem; text-align:center;">
<div style="font-size:2em; margin-bottom:0.4rem;">🛰️</div>
<div style="font-family:'Outfit'; font-size:1.05em; font-weight:600; color:#EDE8DF; margin-bottom:0.5rem;">Evidence-Based</div>
<div style="font-size:0.78em; color:#9DA3B4; line-height:1.5;">Multi-sensor EO pipeline delivers <strong style="color:#C9A96E;">ward-level heat intelligence</strong> unavailable from ground stations alone</div>
</div>

<div style="flex:1; background:#1E2235; border:1px solid rgba(79,196,207,0.3); border-top:3px solid #4FC4CF; border-radius:0 0 4px 4px; padding:1.2rem 1rem; text-align:center;">
<div style="font-size:2em; margin-bottom:0.4rem;">📋</div>
<div style="font-family:'Outfit'; font-size:1.05em; font-weight:600; color:#EDE8DF; margin-bottom:0.5rem;">Policy-Ready</div>
<div style="font-size:0.78em; color:#9DA3B4; line-height:1.5;">Outputs map directly onto <strong style="color:#4FC4CF;">HAP's 4 pillars</strong> and SDG 11 / 13 reporting requirements</div>
</div>

<div style="flex:1; background:#1E2235; border:1px solid rgba(88,214,141,0.3); border-top:3px solid #58D68D; border-radius:0 0 4px 4px; padding:1.2rem 1rem; text-align:center;">
<div style="font-size:2em; margin-bottom:0.4rem;">🔄</div>
<div style="font-family:'Outfit'; font-size:1.05em; font-weight:600; color:#EDE8DF; margin-bottom:0.5rem;">Sustainable</div>
<div style="font-size:0.78em; color:#9DA3B4; line-height:1.5;">GEE-based workflow enables AMC to <strong style="color:#58D68D;">self-update annually</strong> at near-zero marginal cost</div>
</div>

</div>

.pull-left[

.stats-row[

.stat-box.alert[
<span class="stat-number" style="font-size:1.6em;">1,344</span>
<span class="stat-label">Lives lost in one month</span>
<span class="stat-source">May 2010 · The crisis we address</span>
]

.stat-box.teal[
<span class="stat-number" style="font-size:1.6em;">£500k</span>
<span class="stat-label">Total investment</span>
<span class="stat-source">Self-sustaining after Year 1</span>
]

]

]

.pull-right[

> **In 2010, Ahmedabad lost 1,344 lives to a single heat wave. EO-HEAT ensures the city never faces that crisis blind again.**

<br>

.checklist[
- First **ward-level Heat Vulnerability Index** for Ahmedabad
- **Annual self-updating** GEE pipeline — no recurring licence cost
- Directly feeds **HAP annual revision** & SDG 11/13 national reporting
]

<br>

.mono.text-small.text-muted[
github.com/ArthurZhang69/CASA0023-GROUP-PRESENTATION
]

]

.footnote[Azhar et al. (2014) · Hess et al. (2018) · AMC/NRDC (2019) HAP · CASA0023 · UCL 2026 · Slides: Xaringan + R + ggplot2 · All EO data via Google Earth Engine]
