---
title: "EO-HEAT Ahmedabad — Slides 13–15"
subtitle: "Project Plan, Risk Register & Summary"
author: "ZheXiang Zhou · Person E"
output:
  xaringan::moon_reader:
    css: [default, "../custom.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: "16:9"
      countIncrementalSlides: false
      slideNumberFormat: "%current% / %total%"
      navigation:
        scroll: false
    seal: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE,
  fig.retina = 3, fig.align = "center"
)
```

```{r libraries, include=FALSE}
library(ggplot2)
library(scales)
library(showtext)

font_add_google("Cormorant Garamond", "cormorant")
font_add_google("Outfit", "outfit")
showtext_auto()
showtext_opts(dpi = 300)

theme_eoheat <- function(base_size = 14) {
  theme_minimal(base_family = "outfit", base_size = base_size) +
  theme(
    plot.background  = element_rect(fill = "#0F1117", color = NA),
    panel.background = element_rect(fill = "#0F1117", color = NA),
    panel.grid.major = element_line(color = "#252A40", linewidth = 0.4),
    panel.grid.minor = element_blank(),
    text             = element_text(color = "#9DA3B4"),
    axis.text        = element_text(color = "#5C6380", size = rel(0.85)),
    axis.title       = element_text(color = "#9DA3B4", size = rel(0.9)),
    plot.title       = element_text(color = "#EDE8DF", face = "bold",
                                    size = rel(1.1), margin = margin(b = 4)),
    plot.subtitle    = element_text(color = "#9DA3B4", size = rel(0.8),
                                    margin = margin(b = 10)),
    plot.caption     = element_text(color = "#5C6380", size = rel(0.65),
                                    hjust = 0, margin = margin(t = 6)),
    legend.background = element_rect(fill = "#0F1117", color = NA),
    legend.text      = element_text(color = "#9DA3B4"),
    legend.title     = element_text(color = "#EDE8DF"),
    plot.margin      = margin(10, 10, 10, 10)
  )
}
```

---

## Project Timeline

.slide-label[Slide 13a · Project Plan]

.left-wide[

```{r gantt-chart, fig.height=3.8, fig.width=8, out.width="100%"}
lvls <- rev(c("WP0  Stakeholder Scoping & Data Audit",
              "WP1  LST Mapping (Landsat 8/9 TIRS)",
              "WP2  Land Cover & Green Space (Sentinel-2)",
              "WP3  Heat Vulnerability Index",
              "WP4  Dashboard & Deliverables",
              "WP5  Training, Handover & BAU"))

wp <- data.frame(
  label = factor(c("WP0  Stakeholder Scoping & Data Audit",
                    "WP1  LST Mapping (Landsat 8/9 TIRS)",
                    "WP2  Land Cover & Green Space (Sentinel-2)",
                    "WP3  Heat Vulnerability Index",
                    "WP4  Dashboard & Deliverables",
                    "WP5  Training, Handover & BAU"), levels = lvls),
  start = c(1, 2, 3, 5, 7, 9),
  end   = c(2, 5, 6, 8, 10, 12),
  col   = c("#5C6380", "#C9A96E", "#4FC4CF",
            "#58D68D", "#E05C5C", "#9B59B6")
)

# Milestones mapped to the same factor levels
ms <- data.frame(
  month = c(2, 6, 8, 10, 12),
  wp    = factor(c("WP0  Stakeholder Scoping & Data Audit",
                    "WP2  Land Cover & Green Space (Sentinel-2)",
                    "WP3  Heat Vulnerability Index",
                    "WP4  Dashboard & Deliverables",
                    "WP5  Training, Handover & BAU"), levels = lvls),
  tag   = c("Data Audit\nComplete",
            "LST & LULC\nDelivered",
            "HVI Map\nDelivered",
            "Dashboard\nBeta",
            "Final\nHandover")
)

ggplot(wp, aes(y = label)) +
  # Bars
  geom_segment(aes(x = start - 0.1, xend = end + 0.1,
                   yend = label, colour = col),
               linewidth = 7, lineend = "round") +
  # Milestones
  geom_point(data = ms, aes(x = month, y = wp),
             shape = 18, size = 5, colour = "#EDE8DF",
             inherit.aes = FALSE) +
  geom_text(data = ms,
            aes(x = month + 0.35, y = wp, label = tag),
            colour = "#EDE8DF", size = 2.8, family = "outfit",
            fontface = "bold", lineheight = 0.85,
            hjust = 0, vjust = 0.5,
            inherit.aes = FALSE) +
  scale_colour_identity() +
  scale_x_continuous(
    breaks = 1:12, labels = paste0("M", 1:12),
    limits = c(0.5, 14.5), expand = expansion(add = 0)
  ) +
  labs(title = "12-month delivery schedule",
       subtitle = "6 work packages \u00b7 5 key milestones \u00b7 phased around pre-monsoon window (Mar\u2013May)",
       x = NULL, y = NULL) +
  theme_eoheat(base_size = 13) +
  theme(
    panel.grid.major.y = element_blank(),
    axis.text.y  = element_text(size = 10, colour = "#9DA3B4", hjust = 1),
    axis.text.x  = element_text(size = 9, colour = "#5C6380"),
    plot.title    = element_text(size = 13),
    plot.subtitle = element_text(size = 9.5)
  )
```

.fig-caption[Fig. P · Gantt chart — WP0 to WP5 with milestone diamonds]

]

.right-narrow[

<h3 style="font-family:var(--font-body); font-size:1em; font-weight:500; color:var(--gold); text-transform:uppercase; letter-spacing:0.12em; margin-top:0; margin-bottom:0.6rem;">Why this timeline?</h3>

<div style="font-size:0.78em; line-height:1.55; color:var(--text-secondary);">

<p style="margin:0 0 0.55rem 0;"><strong style="color:#EDE8DF;">Pre-monsoon window (Mar–May)</strong><br>Peak heat + cloud cover &lt;15% maximises usable Landsat &amp; Sentinel scenes over Gujarat<br><span style="color:#5C6380; font-size:0.9em;">(Rajeshwari &amp; Mani, 2014)</span></p>

<p style="margin:0 0 0.55rem 0;"><strong style="color:#EDE8DF;">WP0 scoping before analysis</strong><br>UNDP guidance mandates stakeholder mapping &amp; data audit before technical work to prevent scope creep<br><span style="color:#5C6380; font-size:0.9em;">(UNDP, 2021)</span></p>

<p style="margin:0 0 0.55rem 0;"><strong style="color:#EDE8DF;">WP5 overlaps WP4 by 2 months</strong><br>Iterative training alongside dashboard development — World Bank "learning-by-doing" model<br><span style="color:#5C6380; font-size:0.9em;">(World Bank, 2019)</span></p>

<p style="margin:0;"><strong style="color:#EDE8DF;">12 months total</strong><br>Consistent with UNEP/GRID urban heat programme: 10–14 months for city-scale delivery<br><span style="color:#5C6380; font-size:0.9em;">(UNEP, 2023)</span></p>

</div>

]

.footnote[Rajeshwari & Mani (2014) *Int. J. Appl. Eng. Res.* · UNDP (2021) *Project Management Guidance* · World Bank (2019) *Capacity Building Framework* · UNEP (2023) *Beating the Heat* report]

---

## Budget & Value for Money

.slide-label[Slide 13b · Project Plan]

.left-wide[

```{r budget-bar, fig.height=3.5, fig.width=8, out.width="100%"}
budget <- data.frame(
  item   = c("Personnel\n(2 RS analysts + 1 GIS engineer + 1 PM)",
             "Local Partner\n(AMC liaison & field coordination)",
             "Stakeholder Engagement\n(workshops, ward councillor meetings)",
             "Capacity Building & Training\n(AMC staff upskilling, SOP manuals)",
             "Software & Cloud Compute\n(GEE, QGIS, server hosting)",
             "Reporting & Dissemination\n(publications, policy briefs)",
             "Contingency Reserve\n(ring-fenced for overruns)"),
  amount = c(280, 50, 45, 30, 20, 15, 60),
  fill   = c("#C9A96E", "#4FC4CF", "#58D68D",
             "#9B59B6", "#5DADE2", "#F0A04B", "#5C6380")
)
budget$item <- factor(budget$item, levels = rev(budget$item))
budget$lab  <- paste0("\u00a3", budget$amount, "k")
budget$pct  <- paste0(round(budget$amount / 500 * 100), "%")

ggplot(budget, aes(x = amount, y = item, fill = fill)) +
  geom_col(width = 0.55) +
  geom_text(aes(label = lab),
            hjust = -0.12, colour = "#EDE8DF",
            size = 3.8, family = "outfit", fontface = "bold") +
  geom_text(aes(label = pct, x = amount - 3),
            hjust = 1, colour = "#0F1117",
            size = 3.0, family = "outfit", fontface = "bold") +
  scale_fill_identity() +
  scale_x_continuous(expand = expansion(mult = c(0, 0.18))) +
  labs(title = "Budget allocation \u00b7 \u00a3500,000",
       subtitle = "Personnel-led investment typical of technical consultancy; zero EO data licence cost",
       x = NULL, y = NULL) +
  theme_eoheat(base_size = 12) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_line(colour = "#252A40", linewidth = 0.3),
    axis.text.y = element_text(size = 9, colour = "#9DA3B4", hjust = 1,
                               lineheight = 0.9),
    axis.text.x = element_blank(),
    plot.title    = element_text(size = 13),
    plot.subtitle = element_text(size = 9.5)
  )
```

.fig-caption[Fig. Q · Budget breakdown by category with percentage labels]

]

.right-narrow[

<h3 style="font-family:var(--font-body); font-size:1em; font-weight:500; color:var(--gold); text-transform:uppercase; letter-spacing:0.12em; margin-top:0; margin-bottom:0.6rem;">Why this budget?</h3>

<div style="font-size:0.78em; line-height:1.55; color:var(--text-secondary);">

<p style="margin:0 0 0.55rem 0;"><strong style="color:#EDE8DF;">Personnel 56%</strong><br>Consistent with UKRI-funded technical consultancy where specialist staff are the primary cost driver<br><span style="color:#5C6380; font-size:0.9em;">(UKRI, 2022)</span></p>

<p style="margin:0 0 0.55rem 0;"><strong style="color:#EDE8DF;">12% contingency</strong><br>Follows FCDO (formerly DFID) best practice of 10–15% for international development projects<br><span style="color:#5C6380; font-size:0.9em;">(FCDO, 2020)</span></p>

<p style="margin:0 0 0.55rem 0;"><strong style="color:#EDE8DF;">£0 EO data cost</strong><br>All Landsat, Sentinel-2 &amp; MODIS data are open-access via Google Earth Engine — no licensing fee<br><span style="color:#5C6380; font-size:0.9em;">(Gorelick et al., 2017)</span></p>

<p style="margin:0;"><strong style="color:#EDE8DF;">Local partner £50k</strong><br>Embeds AMC liaison from day one, aligning outputs with the Heat Action Plan revision cycle<br><span style="color:#5C6380; font-size:0.9em;">(AMC, 2019)</span></p>

</div>

.chip[56% Personnel] .chip.teal[12% Contingency] .chip[0% EO Licence]

]

.footnote[UKRI (2022) *Full Economic Costing Guide* · FCDO (2020) *Smart Rules* · Gorelick et al. (2017) *Remote Sens. Environ.* 202:18–27 · AMC/NRDC (2019) *Ahmedabad Heat Action Plan*]

---

## Risk Register

.slide-label[Slide 14 · Project Plan]

<table style="width:100%; border-collapse:collapse; font-size:0.82em; margin-top:0.2rem; line-height:1.45;">
<thead>
<tr style="background:#252A40; border-bottom:2px solid rgba(201,169,110,0.4);">
  <th style="padding:0.4rem 0.6rem; color:#C9A96E; font-size:0.78em; letter-spacing:0.08em; text-transform:uppercase; text-align:left; width:3%;">#</th>
  <th style="padding:0.4rem 0.6rem; color:#C9A96E; font-size:0.78em; letter-spacing:0.08em; text-transform:uppercase; text-align:left; width:27%;">Risk Description</th>
  <th style="padding:0.4rem 0.6rem; color:#C9A96E; font-size:0.78em; letter-spacing:0.08em; text-transform:uppercase; text-align:center; width:7%;">Likelihood</th>
  <th style="padding:0.4rem 0.6rem; color:#C9A96E; font-size:0.78em; letter-spacing:0.08em; text-transform:uppercase; text-align:center; width:7%;">Impact</th>
  <th style="padding:0.4rem 0.6rem; color:#C9A96E; font-size:0.78em; letter-spacing:0.08em; text-transform:uppercase; text-align:left; width:56%;">Mitigation Strategy</th>
</tr>
</thead>
<tbody>
<tr style="background:rgba(224,92,92,0.06); border-bottom:1px solid rgba(201,169,110,0.12);">
  <td style="padding:0.35rem 0.6rem; color:#C9A96E; font-weight:600;">R1</td>
  <td style="padding:0.35rem 0.6rem; color:#EDE8DF;">Cloud cover limits usable Landsat&nbsp;8/9 and Sentinel&#8209;2 scenes for LST and land&#8209;cover analysis</td>
  <td style="padding:0.35rem 0.6rem; text-align:center;"><span style="background:#F0A04B; color:#0F1117; padding:0.15em 0.5em; border-radius:3px; font-weight:600; font-size:0.85em;">Med</span></td>
  <td style="padding:0.35rem 0.6rem; text-align:center;"><span style="background:#E05C5C; color:#0F1117; padding:0.15em 0.5em; border-radius:3px; font-weight:600; font-size:0.85em;">High</span></td>
  <td style="padding:0.35rem 0.6rem; color:#9DA3B4;">Acquire in pre&#8209;monsoon dry window (Mar&ndash;May, &lt;15% cloud); gap&#8209;fill with MODIS 8&#8209;day composites</td>
</tr>
<tr style="background:rgba(79,196,207,0.04); border-bottom:1px solid rgba(201,169,110,0.12);">
  <td style="padding:0.35rem 0.6rem; color:#C9A96E; font-weight:600;">R2</td>
  <td style="padding:0.35rem 0.6rem; color:#EDE8DF;">Ward boundaries redrawn between India Census cycles, causing spatial mismatch with demographic data</td>
  <td style="padding:0.35rem 0.6rem; text-align:center;"><span style="background:#58D68D; color:#0F1117; padding:0.15em 0.5em; border-radius:3px; font-weight:600; font-size:0.85em;">Low</span></td>
  <td style="padding:0.35rem 0.6rem; text-align:center;"><span style="background:#F0A04B; color:#0F1117; padding:0.15em 0.5em; border-radius:3px; font-weight:600; font-size:0.85em;">Med</span></td>
  <td style="padding:0.35rem 0.6rem; color:#9DA3B4;">Use Ahmedabad Municipal Corporation (AMC) latest shapefile; automated spatial harmonisation in GEE</td>
</tr>
<tr style="background:rgba(224,92,92,0.06); border-bottom:1px solid rgba(201,169,110,0.12);">
  <td style="padding:0.35rem 0.6rem; color:#C9A96E; font-weight:600;">R3</td>
  <td style="padding:0.35rem 0.6rem; color:#EDE8DF;">Staff turnover at AMC disrupts adoption of routine annual monitoring (business&#8209;as&#8209;usual) after handover</td>
  <td style="padding:0.35rem 0.6rem; text-align:center;"><span style="background:#F0A04B; color:#0F1117; padding:0.15em 0.5em; border-radius:3px; font-weight:600; font-size:0.85em;">Med</span></td>
  <td style="padding:0.35rem 0.6rem; text-align:center;"><span style="background:#E05C5C; color:#0F1117; padding:0.15em 0.5em; border-radius:3px; font-weight:600; font-size:0.85em;">High</span></td>
  <td style="padding:0.35rem 0.6rem; color:#9DA3B4;">Train 5+ staff across 2 AMC departments; deliver Standard Operating Procedure manuals &amp; video tutorials</td>
</tr>
<tr style="background:rgba(79,196,207,0.04); border-bottom:1px solid rgba(201,169,110,0.12);">
  <td style="padding:0.35rem 0.6rem; color:#C9A96E; font-weight:600;">R4</td>
  <td style="padding:0.35rem 0.6rem; color:#EDE8DF;">Personnel costs exceed budget due to extended specialist engagement or currency fluctuation</td>
  <td style="padding:0.35rem 0.6rem; text-align:center;"><span style="background:#58D68D; color:#0F1117; padding:0.15em 0.5em; border-radius:3px; font-weight:600; font-size:0.85em;">Low</span></td>
  <td style="padding:0.35rem 0.6rem; text-align:center;"><span style="background:#E05C5C; color:#0F1117; padding:0.15em 0.5em; border-radius:3px; font-weight:600; font-size:0.85em;">High</span></td>
  <td style="padding:0.35rem 0.6rem; color:#9DA3B4;">Fixed&#8209;term contracts with capped day&#8209;rates; 12% contingency reserve (&pound;60k) ring&#8209;fenced for overruns</td>
</tr>
<tr style="background:rgba(224,92,92,0.06); border-bottom:1px solid rgba(201,169,110,0.12);">
  <td style="padding:0.35rem 0.6rem; color:#C9A96E; font-weight:600;">R5</td>
  <td style="padding:0.35rem 0.6rem; color:#EDE8DF;">Key stakeholders (AMC officials, ward councillors) disengage, delaying feedback on deliverables</td>
  <td style="padding:0.35rem 0.6rem; text-align:center;"><span style="background:#F0A04B; color:#0F1117; padding:0.15em 0.5em; border-radius:3px; font-weight:600; font-size:0.85em;">Med</span></td>
  <td style="padding:0.35rem 0.6rem; text-align:center;"><span style="background:#F0A04B; color:#0F1117; padding:0.15em 0.5em; border-radius:3px; font-weight:600; font-size:0.85em;">Med</span></td>
  <td style="padding:0.35rem 0.6rem; color:#9DA3B4;">Embed dedicated AMC liaison officer in team from Month&nbsp;1; quarterly review workshops</td>
</tr>
<tr style="background:rgba(79,196,207,0.04);">
  <td style="padding:0.35rem 0.6rem; color:#C9A96E; font-weight:600;">R6</td>
  <td style="padding:0.35rem 0.6rem; color:#EDE8DF;">Landsat thermal band (100&nbsp;m) yields insufficient accuracy when aggregated to ward&#8209;level for the Heat Vulnerability Index</td>
  <td style="padding:0.35rem 0.6rem; text-align:center;"><span style="background:#58D68D; color:#0F1117; padding:0.15em 0.5em; border-radius:3px; font-weight:600; font-size:0.85em;">Low</span></td>
  <td style="padding:0.35rem 0.6rem; text-align:center;"><span style="background:#F0A04B; color:#0F1117; padding:0.15em 0.5em; border-radius:3px; font-weight:600; font-size:0.85em;">Med</span></td>
  <td style="padding:0.35rem 0.6rem; color:#9DA3B4;">Cross&#8209;validate with MODIS MOD11A2 &amp; IMD ground stations; report RMSE per ward</td>
</tr>
</tbody>
</table>

<div style="margin-top:0.8rem;"></div>

.footnote[Risk colour key — <span style="background:#E05C5C; color:#0F1117; padding:0.15em 0.5em; border-radius:3px; font-size:0.9em; font-weight:600;">High</span>&ensp;<span style="background:#F0A04B; color:#0F1117; padding:0.15em 0.5em; border-radius:3px; font-size:0.9em; font-weight:600;">Medium</span>&ensp;<span style="background:#58D68D; color:#0F1117; padding:0.15em 0.5em; border-radius:3px; font-size:0.9em; font-weight:600;">Low</span> · 6 dimensions: data quality · administrative · institutional capacity · budget · stakeholder · technical accuracy]

---

## Summary: Why EO-HEAT Ahmedabad?

.slide-label[Slide 15 · Summary & Call to Action]

<div style="display:flex; gap:1.4rem; margin:1rem 0 1.8rem 0;">

<div style="flex:1; background:#1E2235; border:1px solid rgba(201,169,110,0.25); border-top:3px solid #C9A96E; border-radius:0 0 4px 4px; padding:1.4rem 1.2rem; text-align:center;">
<div style="font-size:1.6em; margin-bottom:0.5rem;">&#x1F6F0;&#xFE0F;</div>
<div style="font-family:'Outfit',sans-serif; font-size:1.1em; font-weight:600; color:#EDE8DF; margin-bottom:0.4rem;">Evidence-Based</div>
<div style="font-size:0.85em; color:#9DA3B4; line-height:1.55;">Multi-sensor EO pipeline delivers <strong style="color:#C9A96E;">ward-level heat intelligence</strong> unavailable from ground stations alone</div>
</div>

<div style="flex:1; background:#1E2235; border:1px solid rgba(79,196,207,0.3); border-top:3px solid #4FC4CF; border-radius:0 0 4px 4px; padding:1.4rem 1.2rem; text-align:center;">
<div style="font-size:1.6em; margin-bottom:0.5rem;">&#x1F4CB;</div>
<div style="font-family:'Outfit',sans-serif; font-size:1.1em; font-weight:600; color:#EDE8DF; margin-bottom:0.4rem;">Policy-Ready</div>
<div style="font-size:0.85em; color:#9DA3B4; line-height:1.55;">Outputs map directly onto <strong style="color:#4FC4CF;">HAP's 4 pillars</strong> and SDG 11 / 13 reporting requirements</div>
</div>

<div style="flex:1; background:#1E2235; border:1px solid rgba(88,214,141,0.3); border-top:3px solid #58D68D; border-radius:0 0 4px 4px; padding:1.4rem 1.2rem; text-align:center;">
<div style="font-size:1.6em; margin-bottom:0.5rem;">&#x1F504;</div>
<div style="font-family:'Outfit',sans-serif; font-size:1.1em; font-weight:600; color:#EDE8DF; margin-bottom:0.4rem;">Sustainable</div>
<div style="font-size:0.85em; color:#9DA3B4; line-height:1.55;">GEE-based workflow enables AMC to <strong style="color:#58D68D;">self-update annually</strong> at near-zero marginal cost</div>
</div>

</div>

.pull-left[

> **In 2010, Ahmedabad lost 1,344 lives to a single heat wave. EO-HEAT ensures the city never faces that crisis blind again.**

.checklist[
- First **ward-level Heat Vulnerability Index** for Ahmedabad
- **Annual self-updating** GEE pipeline — no recurring licence cost
- Directly feeds **HAP annual revision** & SDG 11/13 national reporting
]

]

.pull-right[

.stats-row[

.stat-box.alert[
<span class="stat-number">1,344</span>
<span class="stat-label">Lives lost · May 2010</span>
<span class="stat-source">The crisis we address</span>
]

.stat-box.teal[
<span class="stat-number">£500k</span>
<span class="stat-label">Total investment</span>
<span class="stat-source">Self-sustaining after Year 1</span>
]

]

<br>

.mono.text-small.text-muted[
github.com/ArthurZhang69/CASA0023-GROUP-PRESENTATION
]

]

.footnote[Azhar et al. (2014) *PLOS ONE* · Hess et al. (2018) · AMC/NRDC (2019) HAP · CASA0023 · UCL 2026 · Xaringan + R + ggplot2 · All EO via GEE]
